---
title: "Wooldridge - Econometrics - Ch18 - Ex2"
author: "Thalles Quinaglia Liduares"
date: "28/03/2023"
output: html_document
---

(i) Test for a unit root in log(invpc), including a linear time trend and two lags of 
log(invpct). Use a 5% significance level.

Upload package

```{r}
library(wooldridge)
library(tseries)
```

Upload data

```{r}
HSEINV<-wooldridge::hseinv
```

Define variables 

```{r}

log_invpc <- log(HSEINV$invpc)
d1_log_invpc <- diff(log_invpc, lag = 1)
d2_log_invpc <- diff(log_invpc, lag = 2)
time_trend <- 1:length(log_invpc)
```
ADF test

```{r}
adf.test(log_invpc, alternative = "stationary", k = 2)
```

Based on the Adf-Test, the series is stationary in level.

(ii) Use the approach from part (i) to test for a unit root in log(price).

Define variable

```{r}

log_price <- log(HSEINV$price)

```

ADF test

```{r}
adf.test(log_price, alternative = "stationary", k = 2)
```

(iii) Given the outcomes in parts (i) and (ii), does it make sense to test for cointegration 
between log(invpc) and log(price)?

Based on the Adf-Test, the log_price variable, shows an unit-root, hence is non-stationary.

Yes, it makes sense to test for cointegration between log(invpc) and log(price) since they are both non-stationary variables. Cointegration occurs when two or more non-stationary variables are related through a stationary linear combination, which means that they share a long-run relationship. Therefore, if log(invpc) and log(price) are cointegrated, it suggests that they have a long-term equilibrium relationship that can be modeled using a vector error correction model (VECM).