---
title: "Chapter 5 - OLS Asymptotics"
author: "Thalles Quinaglia Liduares"
date: "25/03/2022"
output: html_document
---

# Exercise 5.2

Upload packages


```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r}

data<-wooldridge::gpa2

attach(data)



```


**Use the data in GPA2.RAW for this exercise.**

**(i) Using all 4,137 observations, estimate the equation**

$$colgpa=\beta_0+\beta_1hsperc+\beta_2sat+u$$

**and report the results in standard form**

```{r}

options(scipen=999) # To avoid sci notation

summary(lm1<-lm(colgpa~hsperc+sat))

```


The estimated equation is expressed as follows

$$\widehat{colgpa}=1.39-0.013hsperc+0.0014sat$$

**(ii) Reestimate the equation in part (i), using the first 2,070 observations.**

```{r}

data2<-data[1:2070,] 

summary(lm2<-lm(data2$colgpa~data2$hsperc+data2$sat))

```


In this case, the estimated equation is given by

$$\widehat{colgpa}=1.43-0.012hsperc+0.0014sat$$

**(iii) Find the ratio of the standard errors on hsperc from parts (i) and (ii).**
**Compare this with the result from (5.10).**

```{r}

std1<-0.00054947

std2<-0.00071852

ratio<-round(std1/std2,3)*100

ratio

```

