---
title: "Chapter 5 - OLS Asymptotics"
author: "Thalles Quinaglia Liduares"
date: "29/03/2022"
output: html_document
---

# Exercise 5.5 

Upload package

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(dplyr)

```

Upload database

```{r}

data<-wooldridge::htv

attach(data)

```


**Consider the analysis in Computer Exercise C11 in Chapter 4 using the data in HTV.RAW,**
**where `educ` is the dependent variable in a regression.**

**(i) How many different values are taken on by `educ` in the sample? Does `educ` have a**
**continuous distribution?**

```{r}

distinct_educ<- dplyr::n_distinct(educ)

distinct_educ

```

Distribution of education

```{r}

hist(educ)

```

There are 15 different values from education in the sample. The distribution of
`educ` is discrete.

**(ii) Plot a histogram of `educ` with a normal distribution overlay. Does the distribution**
**of `educ` appear anything close to normal?**

```{r}

educ_mean<-round(mean(educ),2)

educ_sd<-round(sd(educ),2)

hist(educ, density=10, breaks=10, prob=TRUE, 
     xlab="Years of education", ylim=c(0,1), 
     main="normal curve over histogram")
curve(dnorm(x, mean=educ_mean, sd=educ_sd), 
      col="darkblue", lwd=2, add=TRUE, yaxt="n")
```


**(iii) Which of the CLM assumptions seems clearly violated in the model**

$$educ=\beta_0+\beta_1motheduc+\beta_2fatheduc+\beta_2abil+\beta_4abil^2+u$$

**How does this violation change the statistical inference procedures carried out in**
**Computer Exercise C11 in Chapter 4?**

```{r}

summary(lm1<-lm(educ~motheduc+fatheduc+abil+I(abil^2)))

```


In progress...