---
title: "Chapter 5 - OLS Asymptotics"
author: "Thalles Quinaglia Liduares"
date: "24/03/2022"
output: html_document
---


# Exercise 5.1

Upload packages 

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(lmtest)

```

Upload database

```{r}

data<-wooldridge::wage1

attach(data)

```
**Use the data in WAGE1.RAW for this exercise.**

**(i) Estimate the equation**

$$wage=\beta_0+\beta_1educ+\beta_2exper+\beta_3tenure+u$$
**Save the residuals and plot a histogram.**

```{r}

lm1<-lm(wage~educ+exper+tenure)

summary(lm1)


```

Histogram

```{r}

hist(lm1$residuals,
     main="Histogram of residuals",
     xlab="Residuals")

```

Normality of residuals test

```{r}

Box.test(lm1$residuals, type="Ljung-Box") #lm1

```





**(ii) Repeat part (i), but with log(wage) as the dependent variable.**

```{r}

lm2<-lm(lwage~educ+exper+tenure)

summary(lm2)

hist(lm2$residuals,
   main="Histogram of residuals",
    xlab="Residuals")



```
```{r}
Box.test(lm2$residuals, type="Ljung-Box") #lm2
```


**(iii) Would you say that Assumption MLR.6 is closer to being satisfied for the**
**level-level model or the log-level model?**

The first case is more close of a normal distribution of residuals.


