---
title: '#Chapter 1 - Introduction Econometrics - J. Wooldridge'
author: "Thalles Quinaglia Liduares"
date: "04/02/2022"
output: html_document
---




Upload package for data base

 ```{r}
 
 library(wooldridge)
 
 ```

Package for data analysis

```{r, warning=FALSE, message=FALSE} 

library(dplyr)

```

Upload the Database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage1

attach(data)

```

Ex 1 - Use the data in WAGE1.RAW for this exercise

**(i) Find the average education level in the sample. What are the lowest and highest years of education?**

```{r}

mean_educ<-mean(educ)

mean_educ

```

So the medium value for years of education are 12.5 years

```{r}

min_educ<-min(educ)

min_educ

```
The minimum value for years of education are 0.

```{r}

max_educ<-max(educ)

max_educ

```

The maximum value for years of education are 18 years  

**(ii) Find the average hourly wage in the sample. Does it seem high or low?**

```{r}

mean_wage<-mean(wage)

mean_wage

```

The medium salary/hour are $5.89

**(v) How many women are in the sample? How many men?**

```{r}

num_woman <- data %>%
  filter(female ==1) %>%
  summarise(n=n())

num_woman

```

There are 252 woman in the sample

Now, counting the number of mens in the sample

```{r}

num_man <- data %>%
  filter(female ==0) %>%
  summarise(n=n())

num_man

```

There are 274 man in the sample



# Exercise 2 

##Use the data in BWGHT.RAW to answer this question.

```{r}

data2<-wooldridge::bwght

attach(data2)

```

**(i) How many women are in the sample, and how many report smoking during pregnancy?**


**(ii) What is the average number of cigarettes smoked per day? Is the average a good measure of the “typical” woman in this case? Explain.**

``` {r}
mean_cigs<-mean(cigs)

mean_cigs

```

The mean value for smoked cigarretes is 2.08

**(iii) Among women who smoked during pregnancy, what is the average number of cigarettes smoked per day? How does this compare with your answer from part (ii), and why?

```{r}

mean_smoked<-mean(packs)

mean_smoked

```

**(iv) Find the average of fatheduc in the sample. Why are only 1,192 observations used to compute this average?**

```{r}
mean_fatheduc<-mean(fatheduc, na.rm=T)

mean_fatheduc

```

The mean value for father's education is 13.18 years. There's only 1,192 observations in the sample because there's presence of NA's


**(v) Report the average family income and its standard deviation in dollars.**

```{r}

mean_income<-mean(faminc)

mean_income

sd_income<-sd(faminc)

sd_income

```

The mean income value is $29,026 and the sd is $18.730

#Exercise 3 

**EX 3 data in MEAP01.RAW are for the state of Michigan in the year 2001. Use these data to answer the following questions.**


Upload of database

```{r}

data3<-wooldridge::meap01

attach(data3)

```

**(i) Find the largest and smallest values of math4. Does the range make sense? Explain.**

```{r}
larg<-max(math4)

larg

small<-min(math4)

small

```

**How many schools have a perfect pass rate on the math test? What percentage is this of the total sample?**

```{r}

perf_pass_rate<- data3 %>%
  filter(math4==100) %>%
  summarise(n=n())

perf_pass_rate
```
  
There are 38 students with perfect pass rate in the sample

```{r}
share_perf_pass_rate<-((38)/(1823)*100)

share_perf_pass_rate

```

The percentual share of perfect pass rate is 2.08%

**(iii) How many schools have math pass rates of exactly 50%?**

```{r}

pass_rate50<- data3 %>%
  filter(math4==50) %>%
  summarise(n=n())

pass_rate50

```

17 students passed in the exame with grade of 50%
