---
title: "Chapter 10 - Basic Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "24/03/2022"
output: html_document
---


# Exercise 10.12 


Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(tseries)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::phillips

attach(data)
  
```

**(i) Estimate equation (10.2) using all the data in PHILLIPS.RAW and report the**
**results in the usual form. How many observations do you have now?**

Transforming the variables into time series objects

```{r}

inf.ts<-ts(inf, start=1948, frequency = 1)

unem.ts<-ts(unem, start=1948, frequency = 1)

```

Regression estimates

```{r}

lm1<-lm(inf.ts~unem.ts)

summary(lm1)

```


The estimated equation is expressed as follows

$$\widehat{inf_t}=1.05+0.5unem_t$$
In total, are 56 observations, covering the period 1948-2003.

**(ii) Compare the estimates from part (i) with those in equation (10.14). In**
**particular, does adding the extra years help in obtaining an estimated tradeoff** 
**between inflation and unemployment? Explain**

No. Even adding extra years, the estimated model is not yet capable of capture
the theorical tradeoff between inflation and unemployment rate.

**(iii) Now run the regression using only the years 1997 through 2003. How do these**
**estimates differ from those in equation (10.14)? Are the estimates using the most**
**recent seven years precise enough to draw any firm conclusions? Explain.**

Selecting the period between 1997-2003

```{r}

inf.ts.2<-ts(inf, start=1997, end=2003, frequency = 1)

unem.ts.2<-ts(unem, start=1997, end=2003, frequency = 1)

```


```{r}
summary(lm2<-lm(inf.ts.2~unem.ts.2))
```


Now, in this case, the expected tradeoff is in fact captured by the model

The estimated equation is expressed as follows

$$\widehat{inf_t}=8.88-1.43unem_t$$
