---
title: "Chapter 10 - Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "23/03/2022"
output: html_document
---

# Exercise 10.10

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::intdef

attach(data)

```



**Consider the model estimated in (10.15); use the data in INTDEF.RAW.**

**(i) Find the correlation between ``inf` and `def` over this sample period and**
**comment.**

```{r}

round(cor(inf, def),3)

```

The correlation between `inf` and `def` is equal to 9.7% over this sample period.

**(ii) Add a single lag of inf and def to the equation and report the results in the**
**usual form.**

```{r}

lm1<-lm(i3~inf+def+inf_1+def_1)

summary(lm1)

```

The estimated equation is expressed as follows

$$\hat{i3}=1.61+0.34inf_t-0.18def_t+0.38inf_{t-1}+0.56def_{t-1}$$



**(iii) Compare the estimated LRP for the effect of inflation with that in equation**
**(10.15). Are they vastly different?**

In progress.. 

**(iv) Are the two lags in the model jointly significant at the 5% level?**

```{r}
linearHypothesis(lm1, c("inf_1=0","def_1=0"))
```


The null hypothesis is rejected at the 1% significance level. Hence, there's evidence
that this two lagged variables influence the T-3 bill rate.
