---
title: "Chapter 10 - Basic Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "07/03/2022"
output: html_document
---


# Exercise 10.2 

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(car)
library(forecast)
library(seastests)

```
Upload database

```{r, message=FALSE, warning=FALSE}

data1<-wooldridge::barium
  
```


**Use the data in BARIUM.RAW for this exercise.**

**(i) Add a linear time trend to equation (10.22). Are any variables, other than the**
**trend, statistically significant?**

```{r}
lm1<-lm(lchnimp~lchempi+lgas+lrtwex+
          befile6+affile6+afdec6+t, data1)

summary(lm1)
```

In this case, the only variable statisticaly significant is the time trend, `t`, 
at the 1% level.

**(ii) In the equation estimated in part (i), test for joint significance of all variables**
**except the time trend. What do you conclude?**

```{r}

# Vector of restriction to test if all coefficients but t are equal to zero 

rest<-c("lchempi=0","lgas=0","lrtwex=0","befile6=0","affile6=0","afdec6=0" )

car::linearHypothesis(lm1, rest)

summary(lm1)$fstatistic
```

It´s not possible to reject the null hypothesis that coefficients are equal to 0
because the p-value=0.77>0.05.

**(iii) Add monthly dummy variables to this equation and test for seasonality.**
**Does including the monthly dummies change any other estimates or their standard**
**errors in important ways?**

```{r}
# Creating month dummies 

data1[paste0("M", 1:12)] <- as.data.frame(t(sapply(data1$Month, tabulate, 12)))

lm2<-lm(lchnimp~lchempi+lgas+lrtwex+
          befile6+affile6+afdec6+feb+mar+apr+may+jun+jul+aug+
          sep+oct+nov+dec, data1) 

summary(lm2)
```

Implementation of seasonality test

```{r}

fried(data1$chnimp , freq = 12, diff = T, residuals = F, autoarima = T)

isSeasonal(data1$chnimp,freq=12, test="combined")

```
According to above tests, the variable chinese imports (`chnimp`) do not show seasonality.
