---
title: "Chapter 4 - Basic Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "11/03/2022"
output: html_document
---

# Exercise 10.5 

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(seastests)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::ezanders
  
```

**Use the data in EZANDERS.RAW for this exercise. The data are on monthly unemployment**
**claims in Anderson Township in Indiana, from January 1980 through November**
**1988. In 1984, an enterprise zone (EZ) was located in Anderson (as well as other cities**
**in Indiana). [See Papke (1994) for details.]**

**(i) Regress `log(uclms)` on a linear time trend and 11 monthly dummy variables.**
**What was the overall trend in unemployment claims over this period? (Interpret the**
**coefficient on the time trend.) Is there evidence of seasonality in unemployment**
**claims?**

Creating dummy month variables to the existing dataframe

```{r}

data[paste0("M", 1:12)] <- as.data.frame(t(sapply(data$Month, tabulate, 12)))

```

Regression on `log(uclms)`

```{r}

data$t<-c(1:108)

lm1<-lm(luclms~t+jan+feb+mar+apr+may+jun+jul+aug+sep+oct+nov, data)

summary(lm1)



```

The coefficient associated to variable `Trend` is equal to -0.01 and has
statistical significance at the 1% level.

Seasonality tests

```{r}
isSeasonal(data$uclms, test = "combined", freq = 12)

fried(data$uclms, freq = 12, diff = T, residuals = F, autoarima = T)


```

The null hypothesis of no stable seasonality is rejected at the 1% significance
level. 

In both tests, the variable `uclms` presents seasonality.

**(ii) Add ez, a dummy variable equal to 1 in the months Anderson had an EZ, to the**
**regression in part (i). Does having the enterprise zone seem to decrease unemployment**
**claims? By how much? [You should use formula (7.10) from Chapter 7.]**

```{r}

lm2<-lm(luclms~t+jan+feb+mar+apr+may+jun+jul+aug+sep+oct+nov+ez, data)

summary(lm2)
```

