---
title: "Chapter 10 - Basic Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "26/03/2022"
output: html_document
---

# Exercise 10.13

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(tseries)
library(wooldridge)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::minwage

attach(data)

```

**Use the data in MINWAGE.RAW for this exercise. In particular, use the employment**
**and wage series for sector 232 (Men’s and Boys’ Furnishings). The variable `gwage232`**
**is the monthly growth (change in logs) in the average wage in sector 232, `gemp232` is**
**the growth in employment in sector 232, `gmwage` is the growth in the federal minimum**
**wage, and `gcpi` is the growth in the (urban) Consumer Price Index.**

**(i) Run the regression `gwage232` on `gmwage`, `gcpi`. Do the sign and magnitude of**
**$\hat{\beta}_{mwage}$ make sense to you? Explain. Is `gmwage` statistically significant?**

```{r}

summary(lm1<-lm(gwage232~gmwage+gcpi))

```


The estimated equation is expressed as follows

$$\widehat{gwage232}=0.002+0.15gmwage+0.24gcpi$$

For an unit increase in `gmwage`, the growth in average wage in sector 232 is 
aproximatelly $0.15. In empirical terms, we would expect a negative sign for this
coefficient, because a larger minimum wage, tends to decrease the level of
employment, _ceteris paribus_, lowering the average wage of sector.

**(ii) Add lags 1 through 12 of `gmwage` to the equation in part (i). Do you think it is**
**necessary to include these lags to estimate the long-run effect of minimum wage**
**growth on wage growth in sector 232? Explain.**

```{r}
summary(lm2<-lm(gwage232~gmwage_1+gmwage_2+gmwage_3+gmwage_4+gmwage_5+
          gmwage_6+gmwage_7+gmwage_8+gmwage_9+gmwage_10+
          gmwage_11+gmwage_12+gcpi+gmwage))
```

For monthly data, the theory recommends an inclusion of 12 lags to the model.
But, in this specific case, the model do not show a good performance, with almost 
all variables without statistical significance.

**(iii) Run the regression `gemp232` on `gmwage`,`gcpi`. Does minimum wage growth**
**appear to have a contemporaneous effect on `gemp232`?**

```{r}
summary(lm2<-lm(gemp232~gmwage+gcpi))
```


The estimated model do not show any significance.

**(iv) Add lags 1 through 12 to the employment growth equation. Does growth in the**
**minimum wage have a statistically significant effect on employment growth, either**
**in the short run or long run? Explain**

```{r}

summary(lm3<-lm(gemp232~gmwage_1+gmwage_2+gmwage_3+gmwage_4+gmwage_5+
          gmwage_6+gmwage_7+gmwage_8+gmwage_9+gmwage_10+
          gmwage_11+gmwage_12+gcpi+gmwage))
```

Again, the estimated equation do not show any significance.