---
title: "Chapter 10 - Basic Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "22/03/2022"
output: html_document
---

# Exercise 10.11

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(tseries)
library(car)

```
Upload database

```{r}

data<-wooldridge::traffic2

attach(data)

```



**The file TRAFFIC2.RAW contains 108 monthly observations on automobile accidents,**
**traffic laws, and some other variables for California from January 1981 through**
**December 1989. Use this data set to answer the following questions.**

**(i) During what month and year did California’s seat belt law take effect? When** 
**did the highway speed limit increase to 65 miles per hour?**

```{r}

totacc.ts<-ts(totacc, start=c(1981,1), frequency = 12)

fatacc.ts<-ts(fatacc, start=c(1981,1), frequency = 12)

par(mfrow=c(2,1))

plot.ts(totacc.ts,
        ylab="Number of total accidents",
        main="Evolution of total accidents ")

plot.ts(fatacc.ts,
        ylab="Number of fatal accidents",
        main="Evolution of fatal accidents")
```



The number of fatal accidents fall sharply during 1981, but the lowest value of 
serie was reached in the beggining of 1982.

**(ii) Regress the variable `log(totacc)` on a linear time trend and 11 monthly dummy**
**variables, using January as the base month. Interpret the coefficient estimate on**
**the time trend. Would you say there is seasonality in total accidents?**

```{r}

lm1<-lm(ltotacc~feb+mar+apr+may+jun+jul+aug
        +sep+oct+nov+dec+t)

summary(lm1)

```

The coefficient associated to `t` is equal to 0.002. Hence, there's an increase in
`ltotacc` of approximately  0.2% as time passes by, which suggests a presence of
tendency in the serie.

Now, testing the presence of seasonality in the serie.

```{r}
hyp<-c("feb=0", "mar=0", "apr=0", "may=0",
       "jun=0", "jul=0", "aug=0","sep=0", "oct=0",
       "nov=0", "dec=0")

linearHypothesis(lm1,hyp)
```


If all coefficients associated to the month dummies are equal to 0, then is there 
no evidence of seasonality in the serie. But, via F-Test, it's possible to reject
the null hypothesis that all coefficients are jointly equal to 0 at the 1% 
significance level. Hence, there's evidence of seasonality in the serie.

**(iii) Add to the regression from part (ii) the variables wkends, unem, spdlaw, and**
**beltlaw. Discuss the coefficient on the unemployment variable. Does its sign and**
**magnitude make sense to you?**

```{r}
lm2<-lm(ltotacc~feb+mar+apr+may+jun+jul+aug
        +sep+oct+nov+dec+t+wkends+unem+spdlaw
        +beltlaw)

summary(lm2)

```

The coefficient associated to variable `unem` is equal to -0.021 and have 
statistical significance at the 1% level. As `unem` increases, `ltotacc` decreases
which suggests some sense, since individuals in situation of unemployment might have no 
access to a vehicle.

**(iv) In the regression from part (iii), interpret the coefficients on `spdlaw`** 
**and `beltlaw`. Are the estimated effects what you expected? Explain.**

The coefficient associated to `spdlaw` has the expected sign, as limits of velocity
is imposed, there's a tendency in decrease the number of total accidents. In the
other hand, the coefficient sign of `beltlaw` suggests to the contrary. A possible
explanation for this result, is that, as individuals use the belt, they might incur
in high speed velocities, cause the belt causes a sensation of safety.

**(v) The variable `prcfat` is the percentage of accidents resulting in at least one fatality.**
**Note that this variable is a percentage, not a proportion. What is the average of**
**`prcfat` over this period? Does the magnitude seem about right?**



```{r}

round(mean(prcfat),2)*100

```

The mean percentual value of `prcfat` is equal to 89%. It seems, a very high percentage
of fatalities in the total number of car accidents.

**(vi) Run the regression in part (iii) but use prcfat as the dependent variable in**
**place of log(totacc). Discuss the estimated effects and significance of the speed** 
**and seat belt law variables.**

```{r}

options(scipen=999)

lm3<-lm(prcfat~feb+mar+apr+may+jun+jul+aug
        +sep+oct+nov+dec+t+wkends+unem+spdlaw
        +beltlaw)

summary(lm3)

```

In this case, the coefficient sign of `beltlaw` is as expected, but without
statistical significance. The percentual of fatalities increases, as speed law
increases in this case, which is not an expected result in empirical terms.
