---
title: "Chapter 10 - Basic Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "14/03/2022"
output: html_document
---

# Exercise 10.7

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(dplyr)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::consump


```
**Use the data set CONSUMP.RAW for this exercise**

**Estimate a simple regression model relating the growth in real per capita consumption**
**(of nondurables and services) to the growth in real per capita disposable**
**income. Use the change in the logarithms in both cases. Report the results in the**
**usual form. Interpret the equation and discuss statistical significance.**

```{r}

lm1<-lm(log(rcons)~ly, data)

summary(lm1)

```


The estimated equation is expressed as follows

$$\widehat{log(rcons)}=-5.54+1.40log(y)$$

For an increase of 1% in disposal income per capita the consume of goods and
services increases aproximately 1.4%. The both, intercept and $\beta_1$ coefficient
shows statistical significance at the 1% level. The model has an almost perfect fit, 
with R-Squared of 99.3%.

**(ii) Add a lag of the growth in real per capita disposable income to the equation from**
**part (i). What do you conclude about adjustment lags in consumption growth?**

```{r}

lm2<-lm(log(rcons)~lag(ly,1)+lag(ly,0), data)

summary(lm2)
```


In this case, the estimated model is expressed as follows

$$\widehat{log(rcons)}=-5.42+0.57log(y)_t+0.81log(y)_{t-1}$$

**(iii) Add the real interest rate to the equation in part (i). Does it affect** 
**consumption growth?**

```{r}

lm3<-lm(log(rcons)~ly+log(r3),
        data)
summary(lm3)
```

The estimated equation is expressed as follows 

$$\widehat{log(rcons)}=-5.54+1.40log(y)_t-0.006log(r3)_t$$

Hence, for an increase of 1% in real interest rate, the consume decreases by
0.006%.