---
title: "Chapter 10 - Regression Analysis with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "21/03/2022"
output: html_document
---

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::volat

attach(data)

```


# Exercise 10.9 

**Use the data in VOLAT.RAW for this exercise. The variable `rsp500` is the monthly**
**return on the Standard & Poor’s 500 stock market index, at an annual rate. (This**
**includes price changes as well as dividends.) The variable `i3` is the return on** 
**three- month T-bills, and `pcip` is the percentage change in industrial production;** 
**these are also at an annual rate.**

**(i) Consider the equation**

$$rp500_t=\beta_0+\beta_1pcip_t+\beta_2i3_t+u_t$$

**What signs do you think $\beta_1$ and $\beta_2$ should have?**

The expected sign on `pcip` is positive. As this index for industrial 
production increases, the economic activity also tends to increase, _ceteris paribus_. 
So, the index of SP (represented by `rsp500``), tends to increases, as well.

As the interest rate on the treasury increases, it becomes more profitable to 
invest resources in these treasury stocks, _ceteris paribus_. In this way, less 
resources are invested in businesses, which tends to decrease the S&P index. Hence,
the expected sign of this coefficient is negative.


**(ii) Estimate the previous equation by OLS, reporting the results in standard form.**
**Interpret the signs and magnitudes of the coefficients.**

```{r}

lm1<-lm(rsp500~pcip+i3)

summary(lm1)
```


The estimated equation is expressed as follows

$$\widehat{rsp500}=18.84+0.03pcip-1.36i3$$

Hence, the estimated coefficients have the expected sign.

For an unit variation in `pcip` the `rsp500` increases 0.03 points. On the other
hand, for an unit variation in `i3` the `rsp500` decreases by 1.36 points.

**(iii) Which of the variables is statistically significant?**

The `pcip` do not show statistical significance at anyy level. On the other hand,
the variable `i3` shows statistical significance at the 5% level.

**(iv) Does your finding from part (iii) imply that the return on the S&P 500 is**
**predictable? Explain.**

This simple model shows a poor capacity of explain the variation of S & P index.
In more detailed and robust models, the dynamics of S & P index could be more
investigated.


