---
title: "Chapter 7"
author: "Thalles Quinaglia Liduares"
date: '2022-07-18'
output: html_document
---

## Exercise 7.8 

Upload packages

```{r, message=FALSE, warning=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r, message=FALSE, warning=FALSE}

data<-wooldridge::loanapp

attach(data)

```


Use the data in LOANAPP.RAW for this exercise. The binary variable to be explained 
is approve, which is equal to one if a mortgage loan to an individual was approved. The 
key explanatory variable is white, a dummy variable equal to one if the applicant was 
white. The other applicants in the data set are black and Hispanic.To test for 
discrimination in the mortgage loan market, a linear probability model can be used:

$$approve=\beta_0+\beta_1white+ u$$

**(i) If there is discrimination against minorities, and the appropriate factors have been**
**controlled for, what is the sign of $\beta_1$?**

In this case, we expect a positive sign for $\beta_1$

**(ii) Regress approve on white and report the results in the usual form. Interpret the**
**coefficient on white. Is it statistically significant? Is it practically large?**

```{r}

summary(lm(approve~white))

```

The estimated equation is given by 

$$\widehat{approve}=0.7+0.2white$$

Hence, white people have 20% more chances of being approved in a loan request.

**(iii) As controls, add the variables hrat, obrat, loanprc, unem, male, married, dep, sch,**
**cosign, chist, pubrec, mortlat1, mortlat2, and vr. What happens to the coefficient**
**on white? Is there still evidence of discrimination against nonwhites?**

```{r}
summary(lm(approve~hrat+obrat+loanprc+unem+male+married+dep+sch+cosign+chist+
             pubrec+mortlat1+mortlat2+vr+white))
```


In this case, the coefficient of `white` reduces to 0.12 and still significant at the 1% level.

**(iv) Now, allow the effect of race to interact with the variable measuring other**
**obligations as a percentage of income (obrat). Is the interaction term significant?**

```{r}
lm4<- lm(approve~hrat+obrat+loanprc+unem+male+married+dep+sch+cosign+chist+
             pubrec+mortlat1+mortlat2+vr+white+white*obrat)
summary(lm4)
```

Yes, the coefficient associated to interaction term is positive and significant at the 1% level.

**(v) Using the model from part (iv), what is the effect of being white on the probability**
**of approval when obrat = 32, which is roughly the mean value in the sample?**
**Obtain a 95% confidence interval for this effect.**



$$\widehat{approve}=-0.14\cdot(1)+0.008\cdot(32) \approx 0.11$$ 

```{r}
confint(lm4,level = 0.95)
```
 
The 95% confidence interval is equal to [0.003,0.012].
