---
title: "Chapter 7"
author: "Thalles Quinaglia Liduares"
date: '2022-04-23'
output: html_document
---

# Exercise 7.10

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```
Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::nbasal

attach(data)

```

**Use the data in NBASAL.RAW for this exercise**

**(i) Estimate a linear regression model relating points per game to experience in the**
**league and position (guard, forward, or center). Include experience in quadratic**
**form and use centers as the base group. Report the results in the usual form.**

```{r}
summary(lm1<-lm(points~exper+guard+forward+expersq))
```

The estimated equation is expressed as follows

$$\widehat{points}=4.76+1.28exper+2.31guard+1.54forward-0.07exper^2$$

**(ii) Why do you not include all three position dummy variables in part (i)?**

To not incur in dummy variable trap.

**(iii) Holding experience fixed, does a guard score more than a center? How much**
**more? Is the difference statistically significant?**

In this case, `guards` scores 2.31 points more than `center` with statistical significance
equal to 5% level.

**(iv) Now, add marital status to the equation. Holding position and experience fixed,**
**are married players more productive (based on points per game)?**

```{r}
summary(lm2<-lm(points~exper+guard+forward+expersq+marr))
```

Yes, holding others factors fixed, married players scores, on average, 0.58 points more
than single players. However, this value must be interpreted with caution because, there's no
statistical significance at any representative level.

**(v) Add interactions of marital status with both experience variables. In this expanded**
**model, is there strong evidence that marital status affects points per game?**

```{r}
summary(lm3<-lm(points ~ exper + guard + forward + expersq +marr+ marrblck))
```

No, even is this case, there's no suggestion of statistical significance.

**(vi) Estimate the model from part (iv) but use assists per game as the dependent**
**variable. Are there any notable differences from part (iv)? Discuss.**

```{r}
summary(lm4<-lm(assists~exper + guard + forward + expersq +marr+ marrblck))
```

Similarly to the item (v), remains the problem of lack of statistical significance
in the estimated coefficients associated to marital status.