---
title: "Chapter 7"
author: "Thalles Quinaglia Liduares"
date: '2022-07-12'
output: html_document
---

## Exercise 7.7

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage1

attach(data)

```

**(i) Use equation (7.18) to estimate the gender differential when educ = 12.5.**
**Compare this with the estimated differential when educ = 0.**

```{r}

summary(lm1<-lm(lwage~female+educ+female*educ+exper+expersq+tenure+tenursq))

```

The estimated equation is expressed as follows

$$\widehat{log(wage)}=0.38-0.22female+0.08educ+0.02exper-0.0005exper^2+0.031tenure-0.0005tenure-0.005female\cdot educ$$
Holding other factors fixed, for educ=12.5, we have that

$$\widehat{log(wage)}_{men}=0.08(12.5)=1%$$

For woman: $$-0.22(1)+0.08(12.5)-0.005 \cdot (1) \cdot (12.5) \approx 0.72$$

Hence, there's a difference between returns in terms of wage in the magnitude of 28%.

**(ii) Run the regression used to obtain (7.18), but with $female \cdot(educ- 12.5)$ replacing**
**$female \cdot educ$. How do you interpret the coefficient on female now?**

```{r}

v<-female*(educ-12.5)

summary(lm2<-lm(lwage~female+educ+exper+expersq+v+tenure+tenursq))

```

**(iii) Is the coefficient on female in part (ii) statistically significant? Compare this with**
**(7.18) and comment.**

Yes, it's statistically significant at 1% level, because there's more observations 
close to the mean value of education in the sample.

