---
title: "Chapter 7 - Multiple Regression Analysis with Qualitative Information"
author: "Thalles Quinaglia Liduares"
date: '2022-04-20'
output: html_document
---

# Exercise 7.2

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage2

attach(data)

```


**Use the data in WAGE2.RAW for this exercise.**

**(i) Estimate the model**

$$log(wage)=\beta_0+\beta_1educ+\beta_2exper+\beta_3tenure+\beta_4married+\beta_5black+\beta_6south+\beta_7urban+u$$

**and report the results in the usual form. Holding other factors fixed, what is the**
**approximate difference in monthly salary between blacks and nonblacks? Is this**
**difference statistically significant?**

```{r}
summary(lm1<-lm(lwage~educ+exper+tenure+married+black+south+urban))
```

Given the estimated equation, we observe that `black` earns 18.8% less than `nonblacks`, holding other
factors fixed. The difference is statistically significant at the 1% level.

**(ii) Add the variables $exper^2$  and $tenure^2$  to the equation and show that they**
**are jointly insignificant at even the 20% level.**

```{r}

tensq<-tenure*tenure

expsq<-exper*exper

summary(lm2<-lm(lwage ~ educ + exper + tenure + married + black + 
    south + urban + tensq+expsq))
```

```{r}
linearHypothesis(lm2, c("tensq=0","expsq=0"))
```

Indeed, these two variables aren't jointly significant even at the 20% level.

**(iii) Extend the original model to allow the return to education to depend on**
**race and test whether the return to education does depend on race.**

In progress..

**(iv) Again, start with the original model, but now allow wages to differ across four**
**groups of people: married and black, married and nonblack, single and black, and**
**single and nonblack. What is the estimated wage differential between married**
**blacks and married nonblacks?**

In progress..





