---
title: "Chapter 7"
author: "Thalles Quinaglia Liduares"
date: '2022-07-12'
output: html_document
---

## Exercise 7.6 

```{r, warning=F, message=F}

library(wooldridge)
library(lmreg)
library(car)
```
Use the data in SLEEP75.RAW for this exercise. The equation of interest is

```{r}

data<-wooldridge::sleep75

attach(data)

```

**Use the data in SLEEP75.RAW for this exercise. The equation of interest is**

$$sleep=\beta_0+\beta_1totwork+\beta_2educ+\beta_3age+\beta_4age^2+\beta_5yngkid+u$$
**(i) Estimate this equation separately for men and women and report the results in the**
**usual form. Are there notable differences in the two estimated equations?**

```{r}

summary(lm_men<-lm(sleep~totwrk+educ+age+agesq+yngkid, data=subset(data, male==1)))

```

The estimated coefficients for men equation is given by 

$$\widehat{sleep}_{men}=3648.20-0.182totwork-13.05educ+7.15age-0.04age^2+60.38yngkid$$

Now, for the woman case:

```{r}
summary(lm_woman<-lm(sleep~totwrk+educ+age+agesq+yngkid, data=subset(data, male==0)))
```

For woman's case, the estimated coefficients are given by

$$\widehat{sleep}_{woman}=4238.72-0.139totwork-10.205educ-30.35age+0.367age^2-118.28yngkid$$
The coefficients differ very significantly between these two categories.

**(ii) Compute the Chow test for equality of the parameters in the sleep equation for**
**men and women. Use the form of the test that adds male and the interaction terms**
**male?totwrk, …, male?yngkid and uses the full set of observations. What are the**
**relevant df for the test? Should you reject the null at the 5% level?**

```{r}
summary(lm_chow<-lm(sleep~totwrk+educ+age+agesq+yngkid+male+male*totwrk+male*educ
            +male*age+male*agesq+male*yngkid))
```

```{r}
linearHypothesis(lm_chow, c("male=0","totwrk:male=0","educ:male=0","age:male=0","agesq:male=0","yngkid:male =0"))
```

Based on the p-value of the performed hypothesis test we can reject the null that the
coefficients between men and woman are equal at 5% level.



