---
title: "Chapter 7"
author: "Thalles Quinaglia Liduares"
date: '2022-04-21'
output: html_document
---

# Exercise 7.5

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::ceosal1

attach(data)

```
**In Problem 2 in Chapter 4, we added the return on the firm’s stock, `ros`, to a model**
**explaining CEO salary; `ros` turned out to be insignificant. Now, define a dummy**
**variable, `rosneg`, which is equal to one if $ros < 0$ and equal to zero if $ros \geq 0$. Use**
**CEOSAL1.RAW to estimate the model**

$$log(salary)=\beta_0+\beta_1log(sales)+\beta_2roe+\beta_3rosneg+u$$

**Discuss the interpretation and statistical significance of $\hat{\beta_3}$**

Creating dummy variable 

```{r}
data$rosneg<-ifelse(data$ros >= 0, 0, 1)

data$rosneg
```

Model estimation 

```{r}
lm1<-lm(data$lsalary~data$lsales+data$roe+data$rosneg)
```


The estimated equation is expressed as follows

$$\widehat{\log(salary)}=4.29+0.28log(sales)+0.01roe-0.22rosneg$$

If the stock return of the firm declines, the salary of CEO tends to be negatively affected.
The coefficient $\hat{\beta_3}$.
