---
title: "Chapter 7 - Multiple Regression Analysis with Qualitative Information"
author: "Thalles Quinaglia Liduares"
date: '2022-04-20'
output: html_document
---

# Exercise 7.4

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
```

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::gpa2

attach(data)

```

**Use the data in GPA2.RAW for this exercise.**

**(i) Consider the equation**

$$colgpa=\beta_0+\beta_1size+\beta_2size^2+\beta_3hsperc+\beta_4sat \\
+\beta_5female+\beta_6athlete+u$$

**where `colgpa` is cumulative college grade point average, `hsize` is size of high** 
**school graduating class, in hundreds, `hsperc` is academic percentile in graduating** 
**class, `sat` is combined SAT score, `female` is a binary gender variable, and `athlete` is** 
**a binary variable, which is one for student-athletes. What are your expectations for**
**the coefficients in this equation? Which ones are you unsure about?**

Negative expected signs: $hsize^2$

Positive expected signs: `hsize`, `hsperc`, `sat`, `female`, `athlete`.

**(ii) Estimate the equation in part (i) and report the results in the usual form. What is**
**the estimated GPA differential between athletes and nonathletes? Is it statistically**
**significant?**

```{r}

options(scipen=999)

summary(lm1<-lm(colgpa~hsize+hsizesq+hsperc+sat+female+athlete))
```

The athlets students have a GPA of 0.169 higher than non-athlete students, as others
factors remain fixed. The estimate is statistically significant at the 1% level.
The SAT score, is one of the prerequisites for students claim an athlete fellowship.

**(iii) Drop sat from the model and reestimate the equation. Now, what is the estimated**
**effect of being an athlete? Discuss why the estimate is different than that obtained**
**in part (ii).**

```{r}
summary(lm2<-lm(colgpa ~ hsize + hsizesq + hsperc + female + 
    athlete))

```

Now, the coefficient associated to `athlete` becomes much small and non significant.

**(iv) In the model from part (i), allow the effect of being an athlete to differ by gender**
**and test the null hypothesis that there is no ceteris paribus difference between**
**women athletes and women nonathletes.**

In progress..
