---
title: "Chapter 7 - Multiple Regression Analysis with Qualitative Information"
author: "Thalles Quinaglia Liduares"
date: '2022-04-19'
output: html_document
---

# Exercise 7.1

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::gpa1

attach(data)

```

**Use the data in GPA1.RAW for this exercise.**

**(i) Add the variables `mothcoll` and `fathcoll` to the equation estimated in (7.6) and**
**report the results in the usual form. What happens to the estimated effect of PC**
**ownership? Is PC still statistically significant?**

```{r}
summary(lm1<-lm(colGPA~PC+hsGPA+ACT+mothcoll+fathcoll))
```

Given the estimated coefficients, we observe that PC is statistically significant
at the 5% level. The estimate for this coefficient remais almost equal in relation
to the original case.

**(ii) Test for joint significance of `mothcoll` and `fathcoll` in the equation from part (i)**
**and be sure to report the p-value.**

```{r}
linearHypothesis(lm1,c("mothcoll=0","fathcoll=0"))
```

It's not possible to reject the null hypothesis that both `mothcoll` and `fathcoll`
are equal to zero, because the p-value of F-Test is quite large.

**(iii) Add $hsGPA^2$  to the model from part (i) and decide whether this generalization is**
**needed.**

```{r}

hsgpasq<-hsGPA*hsGPA

summary(lm2<-lm(colGPA ~ PC + hsGPA + ACT + mothcoll + fathcoll+hsgpasq))
```


The inclusion of this variable does not increase the accuracy of the model.
