---
title: "Chapter 7 - Multiple Regression Analysis with Qualitative Information"
author: "Thalles Quinaglia Liduares"
date: '2022-04-20'
output: html_document
---

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::mlb1

attach(data)

```


# Exercise 7.3

**A model that allows major league baseball player salary to differ by position is**

$$log(salary)=\beta_0 +\beta_1years+\beta_2gamesyr+\beta_3bavg \\ 
+\beta_4hrunsyr+\beta_5rbisyr+\beta_6runsyr+\beta_7fldperc \\
+\beta_8allstar+\beta_9frstbase+\beta_{10}scndbase \\
+\beta_{11}thrdbase+\beta_{12}shrtstop+\beta_{13}catcher+u$$

**where outfield is the base group**

**(i) State the null hypothesis that, controlling for other factors, catchers and outfielders**
**earn, on average, the same amount. Test this hypothesis using the data in MLB1.RAW**
**and comment on the size of the estimated salary differential.**

The null hypothesis is that $H_0: \beta_{13}=0$ against the alternative $H_1: \beta_{13} \neq 0$

```{r}
summary(lm1<-lm(lsalary~years+gamesyr+bavg+hrunsyr+rbisyr+runsyr+fldperc
                +allstar+frstbase+scndbase+thrdbase+shrtstop+catcher))
```


```{r}
linearHypothesis(lm1, c("catcher=0"))
```

It's possible to reject the null hypothesis at the 10% significance level. Hence, 
there's a gap between the salaries of two analysed categories.

**(ii) State and test the null hypothesis that there is no difference in average salary**
**across positions, once other factors have been controlled for.**

In this case, the null hypothesis is given by 

$$H_0: \beta_i=0 \  \  \ i=9,10,11,12,13$$
```{r}
linearHypothesis(lm1, c("frstbase=0","scndbase=0","thrdbase=0","shrtstop=0","catcher=0"))
```

It's not possible to reject the null hypothesis even at the 10% significance level.

**(iii) Are the results from parts (i) and (ii) consistent? If not, explain what is**
**happening.**

In the first test, there's some evidence of differetiation in salary between categorias. Otherwise, 
in second case, the results suggests absence of discrimination, so the results must be investigated
more depthly.
