---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "01/04/2022"
output: html_document
---

# Exercise 11.8

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(forecast)
library(tseries)


```


Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::phillips

attach(data)

```



**Use the data in PHILLIPS.RAW for this exercise.**

**(i) Estimate an AR(1) model for the unemployment rate. Use this equation to predict**
**the unemployment rate for 2004. Compare this with the actual unemployment**
**rate for 2004. (You can find this information in a recent Economic Report of the**
**President.)**

Transforming `unem` into ts object.

```{r}
unem.ts<-ts(unem, start=1948, end=2003, frequency=1)
```


```{r}

ndiffs(unem.ts)

summary(ar_1<-forecast::Arima(unem, order=c(1,1,0)))

```

Forecast 1-year ahead

```{r}
forecast(ar_1, h=1)
```

The effective unemployment rate of USA in the year 2004 was equal to 5.53%. The
forecast model predicts a rate equal to 6.00%. An error of forecast equal to
6.00-5.53=0.47%

**(ii) Add a lag of inflation to the AR(1) model from part (i). Is `inf_t-1` statistically**
**significant?**

```{r}


ar_2<-Arima(unem.ts, order=c(1,1,0), xreg = inf_1)


```

**(iii) Use the equation from part (ii) to predict the unemployment rate for 2004.**
**Is the result better or worse than in the model from part (i)?**

```{r}

for_inf_2004<-forecast(ar_2, xreg = inf)

for_inf_2004

```
```{r}
plot(for_inf_2004)
```

The unemployment forecasted is 6.68%, which means a larger value than before.


