---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "01/04/2022"
output: html_document
---

# Exercise 11.6

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::inven

attach(data)

```


**Let `invent` be the real value inventories in the United States during year t, let**
**$GDP_t$ denote real gross domestic product, and let $r3_t$ denote the (ex post) real**
**interest rate on threemonth T-bills. The ex post real interest rate is (approximately)**
**$r3_t =i3_t – inf_t$, where $i3_t$ is the rate on three-month T-bills and $inf_t$ is the annual**
**inflation rate [see Mankiw (1994, Section 6.4)]. The change in inventories, $cinvent$,**
**is the inventory investment for the year. The accelerator model of inventory investment** 
**relates $cinven$ to the $cGDP$, the change in GDP:**

$$cinven_t=\beta_0+\beta_1cGDP_t+u_t$$

**where $\beta_1 > 0$. [See, for example, Mankiw (1994), Chapter 17.]**

**(i) Use the data in INVEN.RAW to estimate the accelerator model. Report the results**
**in the usual form and interpret the equation. Is $\hat{\beta}_1$ statistically greater than zero?**

```{r}
summary(lm1<-lm(cinven~cgdp))
```


The estimated equation is expressed as follows

$$\widehat{cinven}_t=2.58+0.15cGDP_t$$

The coefficient associated to `cgdp` is statistically significant at the 1%
level. For an unit increase in `cgdp` the `cinven` variable increases 0.15 units.

**(ii) If the real interest rate rises, then the opportunity cost of holding inventories**
**rises, and so an increase in the real interest rate should decrease inventories.**
**Add the real interest rate to the accelerator model and discuss the results.**

```{r}
summary(lm2<-lm(cinven~cgdp+r3))
```

For an unit increase in `r3` the `cinven` variable decreases by 0.89 units.

**(iii) Does the level of the real interest rate work better than the first difference,**
**$cr3_t$?**

```{r}
summary(lm3<-lm(cinven~cgdp+cr3))
```

No. The variable `r3` performs better than `cr3`.
