---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "30/03/2022"
output: html_document
---

# Exercise 11.2

Upload packages

```{r, warning=FALSE, message=FALSE}
library(tseries)
library(lmreg)
library(wooldridge)
library(car)
```

Upload database

```{r warning=FALSE, message=FALSE}

data<-wooldridge::earns

attach(data)


```

**In Example 11.7, define the growth in hourly wage and output per hour as the change**
**in the natural log: $ghrwage = \Delta log(hrwage)$ and $goutphr = \Delta log(outphr)$.** 
**Consider a simple extension of the model estimated in (11.29):**

$$ghrwage_t=\beta_0+\beta_1goutphr_t+\beta_2goutphr_{t-1}+u_t$$

**This allows an increase in productivity growth to have both a current and lagged**
**effect on wage growth**

**(i) Estimate the equation using the data in EARNS.RAW and report the results in**
**standard form. Is the lagged value of `goutphr` statistically significant?**

```{r}
summary(lm1<-lm(ghrwage~goutphr+goutph_1))
```

The estimated equation is expressed as follows

$$\widehat{ghrwage}_t=-0.01+0.728goutphr_t+0.457goutphr_{t-1}$$

The estimated coefficient associated to the lagged variable $goutphr_{t-1}$ 
is equal to 0.457 and have statistical significance at the 1% level.

**(ii) If $\beta_1 + \beta_2 = 1$, a permanent increase in productivity growth is**
**fully passed on in higher wage growth after one year. Test $H_0: \beta_1 + \beta_2 = 1$** 
**against the two-sided alternative. Remember, one way to do this is to write the **
**equation so that $\theta = \beta_1 + \beta_'2 $appears directly in the model,** 
**as in Example 10.4 from Chapter 10.**

```{r}
linearHypothesis(lm1, c("goutphr+goutph_1=1"))
```

It's not possible to reject the null hypothesis that $\beta_1+\beta_2=1$ because
the p-value associated to the F-Test is equal to 0.366>0.050.

**(iii) Does $goutphr_{t-2}$ need to be in the model? Explain.**

```{r}
summary(lm2<-lm(ghrwage~goutphr+goutph_1+goutph_2))
```


In terms of statistical significance, its not necessary to include the variable
`goutphr_{t-2}` to the model.

