---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "31/03/2022"
output: html_document
---

# Exercise 11.5

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

Upload database

```{r}
data<-wooldridge::fertil3

attach(data)

```

**(i) Add a linear time trend to equation (11.27). Is a time trend necessary in the**
**first difference equation?**

The equation (11.27) is expressed as follows

$$\widehat{\Delta gfr}=0.964-0.36\Delta pe-0.014\Delta pe_{t-1}+0.110\Delta pe_{t-2}$$

```{r}
summary(lm1<-lm(cgfr~pe+pe_1+pe_2+t))
```

The purpose of estimate with variables in differences is remove trend or seasonality
or both. However, in specific cenarios is necessary to include a time trend. 
In this specific item, the inclusion of a time trend do not contribute for a better
performance of the model. The F-Statistic shows that the variables are not jointly 
significant.

**(ii) Drop the time trend and add the variables `ww2` and `pill` to (11.27) (do not**
**differencethese dummy variables). Are these variables jointly significant at the**
**5% level?**

```{r}
summary(lm2<-lm(cgfr~pe+pe_1+pe_2+ww2+pill))
```

Now, the F-Statistic of the estimated model shows jointly significance of variables.

```{r}
linearHypothesis(lm2, c("ww2=0","pill=0"))
```

Yes, it's possible to reject the null hypothesis that these two variables jointly
don't influences the dependent variable.

**(iii) Add the linear time trend, `ww2`, and `pill` all to equation (11.27). What** 
**happens to the magnitude and statistical significance of the time trend as**
**compared with that in part (i)? What about the coefficient on `pill` as compared**
**with that in part (ii)?**

```{r}
summary(lm3<-lm(cgfr~pe+pe_1+pe_2+ww2+pill+t))
```

The coefficient associated to the trend variable is still not significant.
However, the overall significance of the model becomes significant, as p-value<0.05.

The coefficient associated to the `pill` variable changes from -2.69 to -4.36
with statistical significance of 5% in both cases.