---
title: "Chapter 11"
author: "Thalles Quinaglia Liduares"
date: '2022-04-14'
output: html_document
---

# Exercise 11.7

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)
```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::consump
attach(data)

```


**Use CONSUMP.RAW for this exercise. One version of the permanent income hypothesis**
**(PIH) of consumption is that the growth in consumption is unpredictable. [Another version** 
**is that the change in consumption itself is unpredictable; see Mankiw (1994, Chapter 15)** 
**for discussion of the PIH.] Let $gc_t=log(c_t) - log(c_{t-1})$ be the growth in real per capita** 
**consumption (of nondurables and services). Then the PIH implies that $\mathbb{E}(gc_t \mid I_{t-1})= \mathbb{E}(gc_t)$**
**,where $I_{t-1}$ denotes information known at time (t - 1); in this case, t denotes a year.**

**(i) Test the PIH by estimating $gc_t = \beta_0+\beta_1gc_{t-1}+ u_t$.**
**Clearly state the null and alternative hypotheses. What do you conclude ?**

```{r}
summary(lm1<-lm(gc~gc_1))
```

The estimated equation is expressed as follows

$$\widehat{gc}_t=0.01+0.44gc_{t-1}$$

The null hypothesis is that $H_0: \beta_1=0$ and the alternative $H_1: \beta_1 \neq 0$

```{r}
linearHypothesis(lm1, c("gc_1=0"))
```

Based in the p-value of F-Test we can reject the null hypothesis, so the PIH isn't
corroborated.

**(ii) To the regression in part (i) add the variables $gy_{t−1}, i3_{t−1}$, and $inf_{t−1}$. Are these new**
**variables individually or jointly significant at the 5% level? (Be sure to report the**
**appropriate p-values.)**

```{r}

i3_1<-append(diff(i3), NA)

inf_1<-append(diff(inf), NA)

summary(lm2<-lm(gc~gc_1+gy_1+i3_1+inf_1))
```

```{r}
linearHypothesis(lm2, c("gc_1=0","gy_1=0","i3_1=0","inf_1=0"))
```

The explanatory variables are only jointly significant.

**(iii) In the regression from part (ii), what happens to the p-value for the t statistic**
**on $gc_{t−1}$? Does this mean the PIH hypothesis is now supported by the data?**

The coefficient associated to $gc_{t-1}$ is not significant at any level.

**(iv) In the regression from part(ii), what is the F statistic and its associated p-value for**
**joint significance of the four explanatory variables? Does your conclusion about**
**the PIH now agree with what you found in part (i)?**

The p-value of F-Test is equal to 0.0035, hence its possible to reject the null.
However, the coefficients of the model individually dont presents significance, which
means a poor capacity of explain the model.


