---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: '2022-04-17'
output: html_document
---

# Exercise 11.13

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```
Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::beveridge

attach(data)

```


**Use the data in BEVERIDGE.RAW to answer this question. The data set includes**
**monthly observations on vacancy rates and unemployment rates for the U.S. from** 
**December 2000 through February 2012.**

**(i) Find the correlation between `urate` and `urate_1`. Would you say the correlation**
**points more toward a unit root process or a weakly dependent process?**

```{r}

round(100*cor(urate, urate_1, use = "complete.obs"), 2)

```
The correlation between these two variables are very high, almost close to one.
This implies that the variables are not weakly dependent. 

**(ii) Repeat part (i) but with the vacancy rate, `vrate`.**

```{r}

cor(urate, vrate)

```
Similarly, the correlation is quite high, but in this case it is negative.

**(iii) The Beveridge Curve relates the unemployment rate to the vacancy rate, with the**
**simplest relationship being linear:**

$$urate_t=\beta_0+\beta_1vrate_t+u_t$$
where $\beta_1 <0 $ is expected. Estimate $\beta_0$ and $\beta_1$ by OLS and report the results in the 
usual form. Do you find a negative relationship?

```{r}
summary(lm1<-lm(urate~vrate))
```

The estimated equation is expressed as follows 

$$\widehat{urate}_t=17.11-3.74vrate$$
**(iv) Explain why you cannot trust the confidence interval for $\beta_1$ reported by the**
**OLS output in part (iii). [The tools needed to study regressions of this type are**
**presented in Chapter18.]**


As we see, the correlation between these variables are very high, what might implicate of
failure of CLM assumptions.

**(v) If you difference urate and vrate before running the regression, how does the**
**estimated slope coefficient compare with part (iii)? Is it statistically different from** 
**zero? [This example shows that differencing before running an OLS regression is**
**not always a sensible strategy. But we cannot say more until Chapter 18.]**

```{r}

d.urate<-diff(urate)

d.vrate<-diff(vrate)

```
```{r}
summary(lm2<-lm(d.urate~d.vrate))
```


The coefficients vary significantly, however they do not show statistical significance.
