---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "30/03/2022"
output: html_document
---

# Exercise 11.4

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(lmtest)
library(tseries)

```

Upload database

```{r}

data<-wooldridge::phillips

attach(data)

```

**Use the data in PHILLIPS.RAW for this exercise, but only through 1996.**

**(i) In Example 11.5, we assumed that the natural rate of unemployment is constant. An**
**alternative form of the expectations augmented Phillips curve allows the natural rate**
**of unemployment to depend on past levels of unemployment. In the simplest case,**
**the natural rate at time t equals unemt21. If we assume adaptive expectations, we obtain**
**a Phillips curve where inflation and unemployment are in first differences:**

$$\Delta inf=\beta_0+\beta_1 \Delta unem+u$$

**Estimate this model, report the results in the usual form, and discuss the sign,**
**size, and statistical significance of $\hat{\beta}_1$.**

```{r}

diff_inf<-diff(inf)

diff_unem<-diff(unem) 

summary(lm1<-lm(diff_inf~diff_unem)) 

```


The estimated equation is expressed as follows

$$\widehat{\Delta inf}=-0.07-0.83\Delta unem$$
The coefficient associated to the unemployment variable is equal to -0.83
and have statistical significance at the 1% level. For an unit percent increase
in unemployment rate the inflation rate decreases 0.83%.

**(ii) Which model fits the data better, (11.19) or the model from part (i)? Explain.**

The model in (11.19) presents a $R^2$ equal to approximately 10%. In the other hand,
the model in this exercise presents a $R^2$ equal to 13%. In this second case, 
the inclusion of variables in differences might purge trend in the series.


