---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "06/04/2022"
output: html_document
---

# Exercise 11.9

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(tseries)
#library(forecast)

```
Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::traffic2

attach(data)

```

**Use the data in TRAFFIC2.RAW for this exercise. Computer Exercise C11 in Chapter 10**
**previously asked for an analysis of these data.**

**(i) Compute the first order autocorrelation coefficient for the variable `prcfat`.**
**Are you concerned that `prcfat` contains a unit root? Do the same for the unemployment** 
**rate.**

```{r}

prcfat.ts<-ts(prcfat, start=c(1981,1), end=c(1989,12), frequency = 12)

plot.ts(prcfat.ts)

acf(prcfat.ts, pl=F, lag=5)

```
Based on time serie plot of variable `prcfat` and in the respective ACF function, 
there's evidence that this variable is not stationary.

```{r}


unem.ts<-ts(unem, start=c(1981,1), end=c(1989,12), frequency = 12)

plot.ts(unem.ts)

acf(unem, pl=F, lag=5)

```

Similarly for the variable `unem`.

**(ii) Estimate a multiple regression model relating the first difference of prcfat,**
**$\Delta prcfat$, to the same variables in part (vi) of Computer Exercise C11 in Chapter 10,**
**except you should first difference the unemployment rate, too. Then, include a**
**linear time trend, monthly dummy variables, the weekend variable, and the two**
**policy variables; do not difference these. Do you find any interesting results?**

```{r}

unem_1<-diff(unem)

unem_1<-append(unem_1, values=NA, after=length(unem_1)) # To equal the length of 
                                                        #  unem_1 to the length
                                                        # of other variables

lm1<-lm(prcfat~prcfat_1+unem+unem_1+t+feb+mar+
                  apr+may+jun+jul+aug+sep+oct+nov+dec+wkends+
                  spdlaw+beltlaw)


summary(lm1)

```
Based on coefficients associated to months of july and august, seems to have a 
greater impact on traffic accidents.

**(iii) Comment on the following statement: “We should always first difference any**
**time series we suspect of having a unit root before doing multiple regression**
**because it is the safe strategy and should give results similar to using the levels.”**
**[In answering this, you may want to do the regression from part (vi) of Computer**
**Exercise C11 in Chapter 10, if you have not already.]**

Non-stationary series may not satisfy the CLM assumptions. Generally, a differentiation process
is required to make the series stationary and perform the multiple regression estimations.

