---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: "27/03/2022"
output: html_document
---

# Exercise 11.1

Upload packages

```{r, warning=FALSE, message=FALSE}

library(tseries)
library(lmreg)
library(wooldridge)


```

Upload database

```{r}

data<-wooldridge::hseinv

attach(data)

```


**Use the data in HSEINV.RAW for this exercise.**

**(i) Find the first order autocorrelation in log(invpc). Now, find the autocorrelation**
**after linearly detrending log(invpc). Do the same for log( price). Which of the two**
**series may have a unit root?**

```{r}

linvpc.ts<-ts(linvpc, start=1947, end=1988, frequency = 1)

acf(linvpc.ts, pl=FALSE)

```

The first-order autocorrelation on `log(invpc)` is equal to 0.594.

```{r}

linvpc_diff<-diff(linvpc.ts) #Applying first-difference

acf(linvpc_diff, pl=FALSE)

```

Now, the first order autocorrelations reduces from 0.594 to 0.042.

```{r}

par(mfrow=c(2,1))

plot.ts(linvpc.ts)
plot.ts(linvpc_diff)
```


```{r}

lprice.ts<-ts(lprice, start=1947, end=1988, frequency = 1)

```

ACF

```{r}

acf(lprice.ts, pl=FALSE)

```

The first order autocorrelation on variable `log(price)` is equal to 0.896.

Detrending

```{r}

lprice_diff<-diff(lprice.ts)

```

ACF

```{r}
acf(lprice_diff, pl=FALSE)
```

The first order autocorrelation reduces from 0.896 to 0.122.

Based on ACF analysis, both series seems to be integrated of order 1, hence, 
with presence of unit roots.

```{r}

par(mfrow=c(2,1))

plot.ts(lprice.ts)
plot.ts(lprice_diff)

```


**(ii) Based on your findings in part (i), estimate the equation**

$$log(invpc)_t=\beta_0+\beta_1\Delta log(price)_t+\beta_2t+u_t$$
**and report the results in standard form. Interpret the coefficient $\hat{\beta_1}$**
**and determine whether it is statistically significant.**

```{r}

tt<-t[1:41]

summary(lm1<-lm(linvpc_diff~lprice_diff+tt))

```

The estimated model as a whole, its not significant, because the p-value of
F-Statistic is equal to 0.396.






