---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: '2022-04-15'
output: html_document
---

# Exercise 11.11

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)
```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::okun

attach(data)

```



**Okun’s Law—see, for example, Mankiw (1994, Chapter 2)—implies the following**
**relationship between the annual percentage change in real GDP, `pcrgdp`, and**
**the change in the annual unemployment rate, `cunem`:**

$$pcrgdp=3-2\cdot cunem$$

**If the unemployment rate is stable, real GDP grows at 3% annually. For each percentage**
**point increase in the unemployment rate, real GDP grows by two percentage points**
**less. (This should not be interpreted in any causal sense; it is more like a statistical** 
**description.)**

**(i) Use the data in OKUN.RAW to estimate the equation. Do you get exactly 3 for**
**the intercept and -2 for the slope? Did you expect to?**

```{r}
summary(lm1<-lm(pcrgdp~cunem))

lm1$coefficients
```

The estimated equation is expressed as follows

$$\widehat{pcrgdp}_t=3.34-1.89cunem_t$$
The estimated coefficients are almost equal to the effective values.

**(ii) Find the t statistic for testing $H_0: \beta_1=-2$. Do you reject $H_0$ against the**
**two-sided alternative at any reasonable significance level?**

```{r}
linearHypothesis(lm1, c("cunem=-2"))
```

Its not possible to reject the null hypothesis that $\beta_1=-2$ at the 5% 
significance level.

(iii) Find the t statistic for testing $H_0: \beta_0 = 3$. Do you reject $H_0$ at the 5% level against 
the two-sided alternative? Is it a “strong” rejection?

```{r}
linearHypothesis(lm1, c("(Intercept)=3"))
```

In this case, it's possible to reject the null hypothesis at the 5% level of
statistical significance.

**(iv) Find the F statistic and p-value for testing $H_0: \beta_0 = 3, \beta_1 = -2$ against the**
**alternative that $H_0$ is false. Does the test reject at the 10% level? Overall, would you** 
**say the data reject or tend to support Okun’s Law?**

```{r}
linearHypothesis(lm1,c("cunem=-2", "(Intercept)=3"))
```


Based in the p-value of F-Test, its not possible to reject the null hypothesis, so
we do not support the Okun Law in this specific case.

