---
title: "Chapter 11 - Further Issues in Using OLS with Time Series Data"
author: "Thalles Quinaglia Liduares"
date: '2022-04-14'
output: html_document
---

# Exercise 11.3

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

Upload database


```{r, warning=FALSE, message=FALSE}

data<-wooldridge::nyse
attach(data)

```

**(i) In Example 11.4, it may be that the expected value of the return at time t, given** 
**past returns, is a quadratic function of returnt21. To check this possibility, use the**
**data in NYSE.RAW to estimate**

$$return_t=\beta_0+\beta_1return_{t-1}+\beta_2return^2_{t-1}+u_t$$
**report the results in standard form.**

```{r}

retsq<-return_1*return_1

summary(lm1<-lm(return~return_1+retsq))
        
```
The estimated equation is expressed as follows

$$\widehat{return}_t=0.22+0.04return_{t-1}-0.009return^2_{t-1}$$


(ii) State and test the null hypothesis that $\mathbb{E}(return_t \mid return_{t-1})$ does not depend on 
return_{t-1}. (Hint: There are two restrictions to test here.) What do you conclude?

The null hypothesus is that $H_0: \beta_1=\beta_2=0$

```{r}
linearHypothesis(lm1, c("return_1=0","retsq=0"))
```

Based in the p-value of F-Test isn't possible to reject the null hypothesis that
`return` depends on its lagged value. Thus, we cannot corroborate the hypothesis 
of efficient markets.

**(iii) Drop $return^2_{t-1}$ from the model, but add the interaction term $return_{t-1}\cdot return{t-2}$.**
**Now test the efficient markets hypothesis.**

```{r}

return_2<-diff(return_1)

ret_int<-return_1*return_2

summary(lm2<-lm(return~return_1+ret_int))

```

```{r}

linearHypothesis(lm2,c("return_1=0","ret_int=0"))

```

Now, in this case, its possible to reject the null hypothesis, and we can corroborate
the efficient market hypothesis.