---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "23/03/2022"
output: html_document
---

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(car)
library(lmreg)

```

Upload database

```{r}

data<-wooldridge::discrim

attach(data)

```


**Use the data in DISCRIM.RAW to answer this question. (See also Computer Exercise**
**C8 in Chapter 3.)**

**(i) Use OLS to estimate the model**

$$log(psoda)=\beta_0+\beta_1prpblack+\beta_2log(income)+\beta_3prppov+u$$

**and report the results in the usual form. Is $\hat{\beta}_1$ statistically different from**
**zero at the 5% level against a two-sided alternative? What about at the 1% level?**


```{r}

summary(lm1<-lm(lpsoda~prpblck+lincome+prppov))


```


The estimated equation is expressed as follows

$$\widehat{log(psoda)}=-1.46+0.07prpblck+0.13log(income)+0.38prppov$$

```{r}

linearHypothesis(lm1, c("prpblck=0"))

```

The coefficient $\hat{\beta}_1$ is statistically different from zero at the 5%
significance level, but not at the 1% level.


**(ii) What is the correlation between log(income) and prppov? Is each variable**
**statistically significant in any case? Report the two-sided p-values.**

```{r}

round(cor(lincome, prppov, use="complete.obs"),3)

```

Hence, the correlation between these two variables are equal to -83.8%.

The variable `lincome` is statistically significant at the 5% level. Otherwise, 
the variable `prppov` is statistically significant at the 1% level.

**(iii) To the regression in part (i), add the variable `log(hseval)`. Interpret its**
**coefficient and report the two-sided p-value for $H_0: \beta_{log(hseval)}=0$.**

```{r}
summary(lm2<-lm(lpsoda~prpblck+lincome+prppov+lhseval))
```


The coefficient of `lhseval` is statistically different from zero at the 1%
signifficance level, because his p-value<2.67e-11.


```{r}

linearHypothesis(lm2, c("lhseval=0"))

confint(lm2)

```

**(iv) In the regression in part (iii), what happens to the individual statistical**
**significance of log(income) and prppov? Are these variables jointly significant?**
**(Compute a p-value.) What do you make of your answers?**



These both variables are not statistically significant individually at any level.

```{r}
linearHypothesis(lm2, c("lincome=0","prppov=0"))
```

In this case, its possible to reject the null hypothesis only at the 5% level of
significance.

