---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "11/03/2022"
output: html_document
---

# Exercise 4.2

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(car)

```

Upload database

```{r}

data<-wooldridge::lawsch85
  
```

**Use the data in LAWSCH85.RAW for this exercise.**

**(i) Using the same model as in Problem 4 in Chapter 3, state and test the null hypothesis**
**that the rank of law schools has no ceteris paribus effect on median starting salary.**

The hypothesis test on variable `rank` is stated as follows:

$H_0: \beta_5 =0$ and $H_1: \beta_5 \neq 0$

```{r}

lm1<-lm(lsalary~LSAT+GPA+llibvol+lcost+rank, data)

summary(lm1)

```

The estimated coefficient of variable `rank` has p-value<2e-16, so is statistically
different from zero.

**(ii) Are features of the incoming class of students—namely, `LSAT` and `GPA`—individually**
**or jointly significant for explaining salary? (Be sure to account for missing data on `LSAT`**
**and `GPA`.)**

Indidually, `LSAT` do not show statistic significance in explaining the variable `salary`.

But, for an unit increase `GPA` point, the `salary` increases by aproximately 24.7%, to the
significance level of 1%.

Now, testing the joint significance of `LSAT` and `GPA`.

```{r}

linearHypothesis(lm1, c("LSAT=0", "GPA=0"))


```
The p-value of statistic is less than 0.05, so the null hypothesis of restricted model is rejected
to the 1% level of confidence.

**(iii) Test whether the size of the entering class (clsize) or the size of the faculty**
**(faculty) needs to be added to this equation; carry out a single test. (Be careful to**
**account for missing data on clsize and faculty.)**

```{r}

lm2<-lm(lsalary~LSAT+GPA+llibvol+lcost+rank+faculty+clsize, data)

summary(lm2)
  
```

The inclusion of variables `faculty` and `clsize` shows that theses two variables
are not statistically significant. I will proceed a test of joint significance, to analyse
if in fact, these two variables are not good predictors of `salary`.

```{r}
linearHypothesis(lm2, c("faculty=0","clsize=0"))
```

In fact, the p-value of 0.39, reveals that these two variables probabily are equal to
0 in estimated model.

**(iv) What factors might influence the rank of the law school that are not included in**
**the salary regression?**

The variable `Age` of Law School, might influence the results, because older institutions
have more reputation and tends to atract the better students.