---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "14/03/2022"
output: html_document
---

# Exercise 4.5

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::mlb1

```

**Use the data in MLB1.RAW for this exercise.**

**(i) Use the model estimated in equation (4.31) and drop the variable `rbisyr`. What**
**happens to the statistical significance of `hrunsyr`? What about the size of the**
**coefficient on `hrunsyr`?**

Original model (Example 4.31)

```{r}

options(scipen = 999) # To avoid scientific notation

lm0<-lm(lsalary~years+gamesyr+bavg+hrunsyr+rbisyr, data)

summary(lm0)

```


```{r}

lm1<-lm(lsalary~years+gamesyr+bavg+hrunsyr, data)

summary(lm1)

```

In the second estimated model, the variable `hrunsyr` becomes statistically 
significant at the 1% level. In the first model, this variable do not show
statistical significance. The magnitude of coefficient increases from 0.01 
to 0.03.

**(ii) Add the variables `runsyr` (runs per year), `fldperc` (fielding percentage), and**
**`sbasesyr` (stolen bases per year) to the model from part (i). Which of these factors**
**are individually significant?**

```{r}

lm2<-lm(lsalary~years+gamesyr+bavg+hrunsyr+runsyr+
          fldperc+sbasesyr, data)

summary(lm2)

```

In this case, the only variable that shows statistical significance is the `runsyr`
at the 1% level.

**(iii) In the model from part (ii), test the joint significance of `bavg`,** 
**`fldperc`, and `sbasesyr`.**

```{r}

linearHypothesis(lm2, c("bavg=0","fldperc=0","sbasesyr=0"))

```

With base in the p-value of F-Test, we cannot reject the null hypothesis
that this coefficients are jointly different from zero.
