---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "18/03/2022"
output: html_document
---

# Exercise 4.7

Upload packages

```{r, warning=FALSE, message=FALSE}
library(lmreg)
library(dplyr)
library(wooldridge)
```

Upload database

```{r, warning=FALSE, message=FALSE}
data<-wooldridge::twoyear

str(data)
```


**Refer to the example used in Section 4.4. You will use the data set TWOYEAR.RAW.**

**(i) The variable `phsrank` is the person’s high school percentile. (A higher number**
**is better. For example, 90 means you are ranked better than 90 percent of your**
**graduating class.) Find the smallest, largest, and average `phsrank` in the sample.**

```{r}
summary(data$phsrank)
```

The smallest, largest and average value of `phsrank` are 0, 99.0 and 56.16
respectively.



**(ii) Add `phsrank` to equation (4.26) and report the OLS estimates in the usual**
**form. Is `phsrank` statistically significant? How much is 10 percentage points of**
**high school rank worth in terms of wage?**

```{r}
lm1<-lm(lwage~jc+totcoll+exper+phsrank, data)

summary(lm1)
```

The estimated equation is expressed as follows

$$\widehat{log(wage)}=1.45-0.009jc+0.075totcoll+0.004exper+0.0003phsrank$$

The variable `phsrank` do not show statistical significance at any level.

In terms of return to wage, an increase of 10% in `phsrank`, implies in 
0.003% increase wage.

**(iii) Does adding `phsrank` to (4.26) substantively change the conclusions on**
**the returns to two- and four-year colleges? Explain.**

In progress...


**(iv) The data set contains a variable called id. Explain why if you add id to**
**equation (4.17) or (4.26) you expect it to be statistically insignificant. What** 
**is the two-sided p-value?**

In progress...






