---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "21/03/2022"
output: html_document
---

# Exercise 4.8

Upload packages

```{r, warning=F, message=FALSE}

library(wooldridge)
library(lmreg)
library(dplyr)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}
data1<-wooldridge::k401ksubs
```



**The data set 401KSUBS.RAW contains information on net financial wealth (nettfa),**
**age of the survey respondent (age), annual family income (inc), family size ( fsize), and**
**participation in certain pension plans for people in the United States. The wealth and**
**income variables are both recorded in thousands of dollars. For this question, use only**
**the data for single-person households (so fsize = 1).**

**(i) How many single-person households are there in the data set?**

```{r}

single_person<- data1 %>%
  filter(marr == 0) %>%
  summarise(n=n())

single_person

```

Hence, there's 3445 single persons in the sample.

**(ii) Use OLS to estimate the model**

$$nettfa=\beta_0+\beta_1inc+\beta_2age+u$$

**and report the results using the usual format. Be sure to use only the single-person**
**households in the sample. Interpret the slope coefficients. Are there any surprises**
**in the slope estimates?**

```{r}

lm1<-lm(nettfa~age+inc, data1, subset= fsize==1)

summary(lm1)



```


The estimated equation is expressed as follows

$$\widehat{nettfa}=-43.03+0.84age+0.79inc$$
The estimated coefficients have the expected sign. For an unit increase in age
of individuals, the net familiar financial assets, increases by $0.84 (thousands). 
For an increase of \$1 in income, the `nettfa` increases by \$0.8 (thousands).

**(iv) Find the p-value for the test $H_0: \beta_2 = 1$ against $H_1: \beta_2 < 1$.**
**Do you reject $H_0$ at the 1% significance level?**

```{r}

linearHypothesis(lm1, c("inc=1"))

```

Yes. It's possible to reject the null hypothesis at the 1% significance level.

**(v) If you do a simple regression of nettfa on inc, is the estimated coefficient**
**on inc much different from the estimate in part (ii)? Why or why not?**

```{r}
lm2<-lm(nettfa~inc, data1, subset=fsize==1)

summary(lm2)
```

In this case, the estimated equation is expressed as follows

$$\widehat{nettfa}=-10.5+0.82inc$$

This represent a sligth difference in terms of magnitude of coefficients.