---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "24/03/2022"
output: html_document
---

# Exercise 4.10

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)
```

Upload database

```{r}

data<-wooldridge::elem94_95

attach(data)

```


**Use the data in ELEM94_95 to answer this question. The findings can be compared**
**with those in Table 4.1. The dependent variable `lavgsal` is the log of average **
**teacher salary and `bs` is the ratio of average benefits to average salary (by school).**

**(i) Run the simple regression of `lavgsal` on `bs`. Is the estimated slope statistically**
**different from zero? Is it statistically different from -1?**

Regression

```{r}

summary(lm1<-lm(lavgsal~bs))

```

Hypothesis test: different from zero

```{r}
linearHypothesis(lm1, c("bs=0"))
```

It's possible to reject the null hypothesis that the coefficient is equal to 0 at
the 1% significance level.

Hypothesis test: different from -1

```{r}

linearHypothesis(lm1, c("bs=-1"))

```

Isn't possible to reject the null hypothesis that the coefficient is equal to -1, 
because the p-value=0.17>0.05.

**(ii) Add the variables lenrol and lstaff to the regression from part (i). What**
**happens to the coefficient on bs? How does the situation compare with that in**
**Table 4.1?**

```{r}

summary(lm2<-lm(lavgsal~bs+lenrol+lstaff))

```


The coefficient on `bs` changes from -0.79 to -0.60.

**(iii) How come the standard error on the `bs` coefficient is smaller in part (ii)**
**than in part (i)? (Hint: What happens to the error variance versus multicollinearity**
**when `lenrol` and `lstaff` are added?)**

In progress..

**(v) Now add the variable lunch to the regression. Holding other factors fixed, are**
**teachers being compensated for teaching students from disadvantaged backgrounds?**
**Explain.**

```{r}

summary(lm3<-lm(lavgsal~bs+lenrol+lstaff+lunch))

```

No, holding other factors fixed, the effect is negative, besides it's small
magnitude.


