---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "10/03/2022"
output: html_document
---

# Exercise 4.1

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(dplyr)
library(wooldridge)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::vote1

attach(data)

```


**The following model can be used to study whether campaign expenditures affect** 
**election outcomes:**

$$voteA=\beta_0+\beta_1log(expendA)+\beta_2log(expendB)+\beta_3prtystrA+u$$

**where `voteA` is the percentage of the vote received by `Candidate A`, `expendA` and** 
**`expendB` are campaign expenditures by Candidates A and B, and `prtystrA` is a measure**
**of party strength for Candidate A (the percentage of the most recent presidential**
**vote that went to A’s party).**

**(i) What is the interpretation of $\beta_1$?**

This case is known as level-log, and is the percentual variation in voteA, for a 
unit increase in `log(expendA)`.

**(ii) In terms of the parameters, state the null hypothesis that a 1% increase** 
**in A’s expenditures is offset by a 1% increase in B’s expenditures.**

 The null hypothesis is given by $H_0: \beta_{1}+\beta_{2}=0$ and alternative 
 hypothesys by $H_1: \beta_{1}+\beta_{2} \neq 0$.
 
**(iii) Estimate the given model using the data in VOTE1.RAW and report the results**
**in usual form. Do A’s expenditures affect the outcome? What about B’s expenditures?**
**Can you use these results to test the hypothesis in part (ii)?**

```{r}
lm1<-lm(voteA~log(expendA)+log(expendB)+prtystrA, data)

summary(lm1)
```


The estimated model, is given by following equation 

$$\widehat{voteA}=45.07+6.08log(expendA)-6.61log(expendB)+0.15prtystrA$$
The $R^2$ indicates that 79.2% of variability in `voteA` is explaneid by exogenous
variables.

**(iv) Estimate a model that directly gives the t statistic for testing the hypothesis**
**in part (ii). What do you conclude? (Use a two-sided alternative.)**

```{r}


data$expendA<--data$expendB

lm2<-lm(voteA~expendA+expendB+prtystrA, data)

summary(lm2)

```
The coefficient associated to `expendA` is statistically different from zero, as
it's p-value<0.05.
