---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "12/03/2022"
output: html_document
---

# Exercise 4.3

Upload packages

```{r}
library(lmreg)
library(wooldridge)
```
Upload database

```{r}

data<-wooldridge::hprice1

```
**Refer to Computer Exercise C2 in Chapter 3. Now, use the log of the housing price as the**
**dependent variable:**

(i) You are interested in estimating and obtaining a confidence interval for the percentage
change in price when a 150-square-foot bedroom is added to a house. In decimal
form, this is $\theta_1=150\beta_1+\beta_2$. Use the data in HPRICE1.RAW to estimate $\theta_1$.

```{r}

options(scipen=999) # To avoid scientific notation

lm1<-lm(lprice~sqrft+bdrms, data)

summary(lm1)

```
Hence, $\theta_1=150(0.0003)+0.0288=0.0738$

**(ii) Write $\beta_2$ in terms of $\theta_1$ and $\beta_1$ and plug this into the `log(price)` equation.**

Writing $\beta_2$ in terms of $\theta_1$ and $\beta_1$, 

$$\beta_2=\theta_1-150\beta_1$$

Plugging $\beta_2$ in the equation:

$$log(price)=\beta_0+\beta_1sqrft+(\theta_1-150\beta_1)bdrms+u$$
**(iii) Use part (ii) to obtain a standard error for $\hat{\theta_1}$ and use this standard error to**
**construct a 95% confidence interval.**

In progress...


