---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "14/03/2022"
output: html_document
---

# Exercise 4.6

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage2

```

**Use the data in WAGE2.RAW for this exercise.**

**(i) Consider the standard wage equation**

$$log(wage)=\beta_0+\beta_1educ+\beta_2exper+\beta_3tenure+u$$


**State the null hypothesis that another year of general workforce experience has the**
**same effect on `log(wage)` as another year of `tenure` with the current employer.**

In this case, the null hypothesis is expressed as follows

$H_0: \beta_2-\beta_3=0$ and the alternative hypothesis given by 
$H_1: \beta_2-\beta_3 \neq 0$


**(ii) Test the null hypothesis in part (i) against a two-sided alternative, at the** 
**5% significance level, by constructing a 95% confidence interval. What do you conclude?**


```{r}

lm1<-lm(lwage~educ+exper+tenure, data)

summary(lm1)

```
Jointly hypothesis test

```{r}

linearHypothesis(lm1, c("exper=1","tenure=-1"))

```
Hence, with base in the p-value of F-Test, we reject the null hypothesis that 
this two variables have the same effect on return of `log(wage)`.
