---
title: "Chapter 4 - Inference"
author: "Thalles Quinaglia Liduares"
date: "29/03/2022"
output: html_document
---

# Exercise 4.11

Upload packages

```{r, warning=FALSE, message=FALSE}
library(wooldridge)
library(lmreg)
library(car)
```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::htv

attach(data)

```

**Use the data in HTV.RAW to answer this question. See also Computer Exercise C10 in**
**Chapter 3.**

**(i) Estimate the regression model**

$$educ=\beta_0+\beta_1motheduc+\beta_2fatheduc+\beta_3abil+\beta_4abil^2+u$$

**by OLS and report the results in the usual form. Test the null hypothesis that `educ`**
**is linearly related to `abil` against the alternative that the relationship is quadratic.**

```{r}

summary(lm1<-lm(educ~motheduc+fatheduc+abil+I(abil^2)))

```

The estimated equation is expressed as follows 

$$\widehat{educ}=8.2+0.19motheduc+0.10fatheduc+0.40abil+0.05abil^2$$
```{r}

linearHypothesis(lm1, c("I(abil^2)=0"))

```
```{r}
linearHypothesis(lm1, c("abil=0","I(abil^2)=0"))
```

```{r}
linearHypothesis(lm1,c("abil=0"))
```


Based on all combinations of hypothesis tests, its possible to reject the null
that `abil^2` is equal to 0 in the estimated model.

**(ii) Using the equation in part (i), test $H_0: \beta_1 = \beta_2 $ against a **
**two-sided alternative. What is the p-value of the test?**

```{r}
linearHypothesis(lm1, c("motheduc-fatheduc=0"))
```

In this case, its not possible to reject the null hypothesis, because the
p-value associated to F-Test is equal to 0.053>0.05.

**(iii) Add the two college tuition variables to the regression from part (i) and**
**determine whether they are jointly statistically significant.**

```{r}
summary(lm2<-lm(educ ~ motheduc + fatheduc + abil + I(abil^2)+tuit17+tuit18))
```

```{r}
linearHypothesis(lm2, c("tuit17=0","tuit18=0"))
```

Based on the estimated coefficients and the hypothesis test its possible conclude
that both `tuit17` and `tuit18` do not influence the dependent variable `educ`.

**(iv) What is the correlation between `tuit17` and `tuit18`? Explain why using the**
**average of the tuition over the two years might be preferred to adding each separately.**
**What happens when you do use the average?**

Correlation

```{r}
cor(tuit17, tuit18)
```

The extreme high correlation between `tuit17` and `tuit18` equal to 98% might be
causing multicollinearity problems in the estimation. Using, one of the two, or 
the median between them, might be a possible solution to this problem.

**(v) Do the findings for the average tuition variable in part (iv) make sense when**
**interpreted causally? What might be going on?**

```{r}
data$tuit_mean<-(tuit17+tuit18)/2
```
```{r}
summary(lm3<-lm(educ ~ motheduc + fatheduc + abil + I(abil^2) + data$tuit_mean))
```

The inclusion of `tuit_mean` do not show individual significance.
