---
title: "Chapter 6 -"
author: "Thalles Quinaglia Liduares"
date: "31/03/2022"
output: html_document
---

# Exercise 6.1

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r}

data<-wooldridge::kielmc

attach(data)

```

**Use the data in KIELMC.RAW, only for the year 1981, to answer the following questions.**
**The data are for houses that sold during 1981 in North Andover, Massachusetts;**
**1981 was the year construction began on a local garbage incinerator**

**(i) To study the effects of the incinerator location on housing price, consider**
**the simple regression model**

$$log(price)=\beta_0+\beta_1 log(dist)+u$$

**where price is housing price in dollars and `dist` is distance from the house to the**
**incinerator measured in feet. Interpreting this equation causally, what sign do you**
**expect for $\beta_1$ if the presence of the incinerator depresses housing prices? Estimate**
**this equation and interpret the results.**

```{r}
summary(lm1<-lm(lprice~ldist))
```

The estimated equation is expressed as follows

$$\widehat{log(price)}=8.25+0.31log(dist)$$
In theory, the expected sign would be negative. However, the estimated coefficient
for `dist` is positive. In this case, there's a postive relatioshinp between the 
distance of incinerator and the houses.

**(ii) To the simple regression model in part (i), add the variables log(intst), log(area),**
**log(land), rooms, baths, and age, where `intst` is distance from the home to the interstate,**
**area is square footage of the house, land is the lot size in square feet, rooms is**
**total number of rooms, baths is number of bathrooms, and age is age of the house in**
**years. Now, what do you conclude about the effects of the incinerator? Explain why**
**(i) and (ii) give conflicting results.**

```{r}
summary(lm2<-lm(lprice~ldist+lintst+larea+lland+rooms+baths+age))
```


In this case, the magnitude of coefficient associated to the `dist` variable is 
very small, equal to 0.02, despites it's positive sign. The others explanatory
variables has expected signs.

**(iii) Add $[log(intst)]^2$ to the model from part (ii). Now what happens? What do**
**you conclude about the importance of functional form?**

```{r}


summary(lm3<-lm(lprice ~ ldist + lintst + larea + lland + rooms + 
    baths + age + lintstsq))
```

There's a considerable increase in the $R^2$ of the estimated equation, equal to
61.78% and almost all variables has statistical significance in this case.

**(iv) Is the square of log(dist) significant when you add it to the model from**
**part (iii)?**

```{r}

ldist_sqr<-ldist^2

summary(lm4<-lm(lprice ~ ldist + lintst + larea + lland + rooms + 
    baths + age + lintstsq+ldist_sqr))
```


No. The square of `log(dist)` isn't significant at any level.