---
title: "Chapter 6 -"
author: "Thalles Quinaglia Liduares"
date: '2022-04-12'
output: html_document
---

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
```


Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::hprice1

attach(data)

```


**Use the data in HPRICE1.RAW for this exercise.**

**(i) Estimate the model**

$$price=\beta_0+\beta_1lotsize+\beta_2sqrft+\beta_3bdrms+u$$

**and report the results in the usual form, including the standard error of the**
**regression. Obtain predicted price, when we plug in `lotsize` = 10,000, `sqrft` =**
**2,300, and `bdrms` = 4; round this price to the nearest dollar**.

```{r}

options(scipen=999) # To avoid scientific notation

summary(lm1<-lm(price~lotsize+sqrft+bdrms))

```

The estimated equation is expressed as follows

$$\widehat{price}=-21.77+0.002lotsize+0.122sqrft+13.85bdrms$$

Substituing the values in the estimated equation, we have that

$$\widehat{price}=-21.77+0.002(10000)+0.122(2300)+13.85(4)$$
$$\widehat{price}=  335 \ dollars$$
**(ii) Run a regression that allows you to put a 95% confidence interval around the**
**predicted value in part (i). Note that your prediction will differ somewhat due to**
**rounding error.**

Defining the transformed variables.

```{r}
lotsize0<-lotsize-10000
sqrft0<-sqrft-2300
bdrms0<-bdrms-4
```

Regressing the transformed variables

```{r}
summary(lm2<-lm(price~lotsize0+sqrft0+bdrms0))
```


The confidence interval is given by $$336.7 \pm 1.96(7.374)$$


Hence, the estimate lies in the interval [322.2,351.15].

**(iii) Let $price^0$ be the unknown future selling price of the house with the characteristics**
**used in parts (i) and (ii). Find a 95% CI for $price^0$ and comment on the width of**
**this confidence interval.**

In progress..

