---
title: "Chapter 6 -"
author: "Thalles Quinaglia Liduares"
date: "05/04/2022"
output: html_document
---

# Exercise 6.5

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```


Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::hprice1

attach(data)

```

**Use the housing price data in HPRICE1.RAW for this exercise.**

**(i) Estimate the model**

$$log(price)=\beta_0+\beta_1(lotsize)+\beta_2log(sqrft)+\beta_3bdrms+u$$

**and report the results in the usual OLS format.**

```{r}

options(scipen=999) # to avoid sci notation

summary(lm1<-lm(lprice~lotsize+lsqrft+bdrms))

```

The estimated equation is expressed as follows

$$\widehat{log(price)}=-0.427+0.000006lotsize+0.777log(sqrft)+0.03bdrms$$
**(ii) Find the predicted value of `log(price)`, when `lotsize` = 20,000, sqrft = 2,500, and**
**`bdrms` = 4. Using the methods in Section 6.4, find the predicted value of price at**
**the same values of the explanatory variables.**

$$\widehat{log(price)}=-0.427+0.000006(20,000)+0.777log(2,500)+0.03(4)$$
$$\widehat{log(price)}=5.89$$
**(iii) For explaining variation in price, decide whether you prefer the model from part (i)**
**or the model**

$$price=\beta_0+\beta_1lotsize+\beta_2sqrft+\beta_3bdrms$$

```{r}
summary(lm2<-lm(price~lotsize+sqrft+bdrms))
```


The logarimization of variables permits interpret coefficients of differents
measures and sizes in one common scale. In this case, the interpretion of coefficients
as percent changes, is more interesting and appropriate.