---
title: "Chapter 6 - Multiple Regression Analysis: Further Issues"
author: "Thalles Quinaglia Liduares"
date: "01/04/2022"
output: html_document
---

# Exercise 6.2

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)
library(car)

```
Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage1

attach(data)

```



**Use the data in WAGE1.RAW for this exercise.**

**(i) Use OLS to estimate the equation**

$$log(wage)=\beta_0+\beta_1educ+\beta_2exper+\beta_3exper^2+u$$

**and report the results using the usual format.**

```{r}
summary(lm1<-lm(lwage~educ+exper+expersq))
```

The estimated equation is expressed as follows

$$\widehat{log(wage)}=0.12+0.09educ+0.04exper-0.0007exper^2$$

All coefficients (except the intercept) are statistically significant at the
1% level.

**(ii) Is $exper^2$ statistically significant at the 1% level?**

Yes, as showed above.

**(iii) Using the approximation**

$$\%\widehat{\Delta wage} \approx 100(\hat{\beta}_2+2\hat{\beta_3}exper)\Delta exper$$

**find the approximate return to the fifth year of experience. What is the approximate**
**return to the twentieth year of experience?**

$$\%\widehat{\Delta wage} \approx 100(0.04+2 \cdot(-0.0007)\cdot5)\cdot(5-4)$$
Hence, the percentual variation is equal to 3.3%. In the second case, substituing
5 by 20, we obtain a value 1.34%. So, there's a dimininshing increase in wage as
experience increases.

**(iv) At what value of exper does additional experience actually lower predicted**
**log(wage)? How many people have more experience in this sample?**

In this case, is necessary to derive the expression in relation to `exper` and equal
to 0 to find the point of inflexion. The expression is given by

$$\frac{\widehat{\Delta wage}}{\Delta exper}=0.04-2\cdot0.0007\cdot exper=0$$
$$exper^*=\frac{0.04}{2\cdot(0.0007)} \approx28.5$$

Thus, with approximately 28.5 years of experience, the salary return starts to decrease.

