---
title: 'Chapter 6 - Multiple Regression Analysis: Further Issues'
author: "Thalles Quinaglia Liduares"
date: "03/04/2022"
output: html_document
---

# Exercise 6.4

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)

```

Upload database


```{r, warning=FALSE, message=FALSE}

data<-wooldridge::gpa2

attach(data)

```

**Use the data in GPA2.RAW for this exercise.**
**(i) Estimate the model**

$$sat=\beta_0+\beta_1hsize+\beta_2hsize^2+u$$

**where `hsize` is the size of the graduating class (in hundreds), and write the results**
**in the usual form. Is the quadratic term statistically significant?**

```{r}

summary(lm1<-lm(log(sat)~hsize+hsizesq))
```

The estimated equation is expressed as follows

$$\widehat{log(sat)}=6.89+0.019hsize-0.002hsize^2$$
The coefficient associated to `hsize^2` is statistically significant at the 1%
level.

**(ii) Using the estimated equation from part (i), what is the “optimal” high school**
**size? Justify your answer.**

Deriving the equation in relation to the `hsize` and setting equal to 0 to find
the optimal value

$$\frac{\partial log(sat)}{\partial hsize}=0.019-2\cdot0.002hsize=0$$

$$hsize^*=\frac{0.019}{2\cdot0.002}$$

$$hsize^*=4.75$$

**(iii) Is this analysis representative of the academic performance of all high school**
**seniors? Explain.**

No. In terms of $R^2$ the model explain just 0.7% of the variability of `sat`, which
is in fact,  a very low power of explanation.

**(iv) Find the estimated optimal high school size, using log(sat) as the dependent**
**variable. Is it much different from what you obtained in part (ii)?**

Already done, to smooth the estimated coefficients, the `log(sat)` was used.