---
title: "Chapter 6 -"
author: "Thalles Quinaglia Liduares"
date: '2022-04-19'
output: html_document
---

# Exercise 6.10

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(dplyr)

```
Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::bwght2

attach(data)

```

**Use the data in BWGHT2.RAW for this exercise.**

**(i) Estimate the equation**



$$log(bwght)=\beta_0+\beta_1npvis+\beta_2npvis^2+u$$

**by OLS, and report the results in the usual way. Is the quadratic term significant?**

```{r}
summary(lm1<-lm(lbwght~npvis+npvissq))
```

The estimated equation is expressed as follows

$$\widehat{log(bwght)}=7.95+0.018npvis-0.0004npvis^2$$
The coefficient associated to variable $npvis^2$ is significant at the 1% level.

**(ii) Show that, based on the equation from part (i), the number of prenatal visits that**
**maximizes `log(bwght)` is estimated to be about 22. How many women had at least**
**22 prenatal visits in the sample?**

Maximizing the above equation in relation to `npvis`, we have that

$$\frac{\partial \widehat{log(bwght)}}{\partial npvis}=0.018-2\cdot(0.0004)npvis=0$$
$$npvis^*=\frac{0.018}{2\cdot(0.0004)}=22.5$$
```{r}
npvis_22<- data %>%
  filter(npvis >= 22) %>%
  summarise(n=n())

npvis_22
```

In the sample, 21 woman's had at least 22 prenatal visits.

**(iv) Add mother’s age to the equation, using a quadratic functional form. Holding**
**npvis fixed, at what mother’s age is the birth weight of the child maximized? What**
**fraction of women in the sample are older than the “optimal” age?**

```{r}
summary(lm2<-lm(lbwght~npvis+npvissq+mage+magesq))
```

Maximizing the above equation in relation to mother's age variable, we have that

$$\frac{\partial \widehat{log(bwght)}}{\partial mage}=0.025-2\cdot(0.0004)mage=0$$
$$mage^*=\frac{0.025}{2\cdot(0.0004)}=31.25$$

Hence, the age's woman that maximize the `log(bwght)` is 31 years.

```{r}
mage_31 <- data %>%
  filter(mage > 31) %>%
  summarise(n=n())

mage_31


```
In the sample, there's a total of 605 womans with age larger than 31 years.

**(v) Would you say that mother’s age and number of prenatal visits explain a lot of the**
**variation in log(bwght)?**

No. In terms of R-Squared, these two variables presents a poor capacity of explain 
the variability in `log(bwght)`.

**(vi) Using quadratics for both npvis and age, decide whether using the natural log or**
**the level of bwght is better for predicting bwght.**

Without log

```{r}
summary(lm3<-lm(bwght~npvis+npvissq+mage+magesq))
```

The model performs well with dependent variable in log form.
