---
title: 'Chapter 6 - Multiple Regression Analysis: Further Issues'
author: "Thalles Quinaglia Liduares"
date: '2022-04-17'
output: html_document
---

# Exercise 6.11

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(dplyr)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::apple

attach(data)

```

**(i) Run the regression `ecolbs` on `ecoprc`, `regprc` and report the results in the usual**
**form, including the R-squared and adjusted R-squared. Interpret the coefficients on**
**the price variables and comment on their signs and magnitudes.**

```{r}

summary(lm1<-lm(ecolbs~ecoprc+regprc))

```

The estimated equation is expressed as follows

$$\widehat{ecolbs}=1.96-2.92ecoprc+3.02regprc$$
The R-Squared and Adjusted R-Squared are equal to 3.6% and 3.3%, respectively.

**(ii) Are the price variables statistically significant? Report the p-values for the**
**individual t tests.**

All coefficients presents statistical significance at the 1% level.

**(iii) What is the range of fitted values for `ecolbs`? What fraction of the sample reports**
**ecolbs = 0? Comment.**

```{r}

ecolbs0<-data %>%
  dplyr::filter(ecolbs == 0) %>%
  summarise(n=n())

share0<-round(100*ecolbs0/length(ecolbs),2)

share0

```

The percentual of values equal to zero are 37.58%.

```{r}
summary(lm1$fitted.values)
```
The interval for `ecolbs` are equal to [0.85, 2.08].

**(iv) Do you think the price variables together do a good job of explaining variation in**
**`ecolbs`? Explain.**

In terms of R-Squared, these two variables, together, presents a low capacity of
explaining the variability of dependent variable `ecolbs`.

**(v) Add the variables `faminc`, `hhsize` (household size), `educ`, and `age` to the regression**
**from part (i). Find the p-value for their joint significance. What do you conclude?**

```{r}
summary(lm2<-lm(ecolbs~ecoprc+regprc+faminc+hhsize+educ+age))
```

```{r}
linearHypothesis(lm2, 
                 c("ecoprc=0",
                   "regprc=0",
                   "faminc=0",
                   "hhsize=0",
                   "educ=0",
                   "age=0"))
```


The p-value of F-Test is equal to 0.00015. Hence, we reject the null hypothesis
that all coefficients are equal to 0.

**(vi) Run separate simple regressions of `ecolbs` on `ecoprc` and then `ecolbs` on `regprc`.**
**How do the simple regression coefficients compare with the multiple regression**
**from part (i)? Find the correlation coefficient between `ecoprc` and `regprc` to help**
**explain your findings.**

```{r}
summary(lm3<-lm(ecolbs~ecoprc))
```
```{r}
summary(lm4<-lm(ecolbs~reglbs))
```


```{r}

cor(ecolbs, ecoprc, use="complete.obs")

cor(ecolbs, reglbs, use="complete.obs")

```

