---
title: 'Chapter 6 - Multiple Regression Analysis: Further Issues'
author: "Thalles Quinaglia Liduares"
date: '2022-04-13'
output: html_document
---

# Exercise 6.9

Upload packages

```{r, warning=F, message=FALSE}

library(wooldridge)
library(lmreg)
library(car)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::nbasal
attach(data)

```



**The data set NBASAL.RAW contains salary information and career statistics for**
**269 players in the National Basketball Association (NBA)**.

**(i) Estimate a model relating points-per-game (points) to years in the league (exper),**
**age, and years played in college (coll). Include a quadratic in exper; the other**
**variables should appear in level form. Report the results in the usual way.**

```{r}
summary(lm1<-lm(points~exper+age+coll+expersq))
```

The estimated equation is expressed as follows

$$\widehat{points}=35.21+2.36exper-1.07age-1.28coll-0.07exper^2$$
**(ii) Holding college years and age fixed, at what value of experience does the next**
**year of experience actually reduce points-per-game? Does this make sense?**

Deriving the estimated equation in relation to the variable `exper`, to find the
point of inflection.

$$\frac{\partial \widehat{points}}{\partial exper}= 2.36-2(0.07)exper=0$$
$$exper^*=\frac{2.36}{2(0.07)} \approx 17$$
Hence, the number of points starts to decline with 17 years of experience. However, this
value do not make practical sense.


**(iv) Add a quadratic in age to the equation. Is it needed? What does this appear to**
**imply about the effects of age, once experience and education are controlled for?**

```{r}
summary(lm2<-lm(points~exper+age+coll+expersq+agesq))
```

In this case, the inclusion of variable `agesq` demonstrates that the points in the match
increases until certain age, and then becomes to decreasing.

**(v) Now regress `log(wage)` on `points`, `exper`, `exper^2`, `age`, and `coll`.**
**Report the results in the usual format.**

```{r}
summary(lm3<-lm(lwage~points+exper+expersq+age+coll))
```

The estimated equation is expressed as follows

$$\widehat{log(wage)}=6.77+0.07points+0.21exper-0.007exper^2-0.04age-0.04coll$$
**(vi) Test whether `age` and `coll` are jointly significant in the regression from part (v).**
**What does this imply about whether age and education have separate effects on**
**wage, once productivity and seniority are accounted for?**

```{r}
linearHypothesis(lm3, c("age=0","coll=0"))
```

It's not possible to reject the null hypothesis that both coefficients are equal
to zero.
