---
title: "Chapter 3 - The Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "22/02/2022"
output: html_document
---
# Exercise 3.5

Upload packages

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage1

attach(data)

```

**5. Confirm the partialling out interpretation of the OLS estimates by explicitly doing the**
**partialling out for Example 3.2. This first requires regressing educ on exper and tenure**
**and saving the residuals, $\hat{r}_1$ . Then, regress log(wage) on  $\hat{r}_1$. Compare the coefficient on $\hat{r}_1$ with the** **coefficient on educ in the regression of log(wage) on educ, exper, and tenure.**

Firstly, estimating `educ` against `exper` and `tenure` and saving the residuals in the variable `res`.

```{r}

lm1<-lm(educ~exper+tenure)
summary(lm1)

res<-lm1$residuals
```
Now, I will regress `log(wage)` on `res` 

```{r}

lm2<-lm(log(wage)~res)

summary(lm2)

```

Finally, in order to analyze the results with original model

```{r}
lm3<-lm(log(wage)~educ+exper+tenure)

summary(lm3)
```

The both estimated coefficients of $\hat{r}_1$ and `educ` is equal to 0.092.