---
title: "Chapter 3 - The Multiple Regression Model - Estimation"
author: "Thalles Quinaglia Liduares"
date: "01/03/2022"
output: html_document
---

# Exercise 3.7

Upload packages

```{r, message=FALSE, warning=FALSE}

library(lmreg)
library(wooldridge)

```

Upload database

```{r, warning=FALSE, message=FALSE}
data<-wooldridge::meap93

attach(data)
```

**Use the data in MEAP93.RAW to answer this question.**

**(i) Estimate the model**

$$math10=\beta_0+\beta_1log(expend)+\beta_2lnchprg+u$$
**and report the results in the usual form, including the sample size and R-squared.**
**Are the signs of the slope coefficients what you expected? Explain.**

```{r}
lm1<-lm(math10~lexpend+lnchprg)

summary(lm1)
```

The estimated equation is given by $$math10=-20.36+6.22lexpend-0.30lnchprg$$

The coefficient of `lexpend` has the expected sign, but the coefficient of `lnchprg`, similary to the example 2.12 
still have negative sign. Hence, the problem of ommited variables might persists in this case.

The variability in `math10` is just around 18% explaneid by this specific model. The sample size is equal to 408 observations.

**(ii) What do you make of the intercept you estimated in part (i)? In particular, does**
**it make sense to set the two explanatory variables to zero? [Hint: Recall that**
**log(1)=0.]**


The intercept represents the value of math exam if `lexpend` and `lnchprg` were equal to 0. In this case, 
the estimated intercept is not statistically significant, cause a negative value for exam grade do not make sense.

**(iii) Now run the simple regression of math10 on log(expend), and compare the slope**
**coefficient with the estimate obtained in part (i). Is the estimated spending effect**
**now larger or smaller than in part (i)?**

```{r}
lm2<-lm(math10~lexpend)

summary(lm2)

```
Now, the coefficient is quite larger in relation to the multiple regression model. A difference of 4.94


**(iv) Find the correlation between lexpend = log(expend) and lnchprg. Does its sign**
**make sense to you?**

```{r}
cor(lexpend, lnchprg)
```
The correlation between these two variables is negative. Hence, if one increase, other decreases, what might explains 
the obtained values in item (iii).





