---
title: "Chapter 3 - The Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "27/02/2022"
output: html_document
---

# Exercise 6

Upload packages 

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::wage2
attach(data)
```

**Use the data set in WAGE2.RAW for this problem. As usual, be sure all of the following**
**regressions contain an intercept.**

**(i) Run a simple regression of IQ on educ to obtain the slope coefficient, say, $\tilde{\delta}$**

```{r}

lm1<-lm(data$IQ~data$educ)

summary(lm1)

```
The coefficient $\tilde{\delta}$ is equal to 3.53.  

**(ii) Run the simple regression of log(wage) on educ, and obtain the slope coefficient, $\tilde{\beta}_1$.**

```{r}

lm2<-lm(data$lwage~data$educ)

summary(lm2)
```
The $\tilde{\beta}_1$ is equal to 0.05.

**(iii) Run the multiple regression of log(wage) on educ and IQ, and obtain the**
**slope coefficients, $\tilde{\beta}_1$ and $\tilde{\beta}_2$ , respectively.**

```{r}
lm3<-lm(data$lwage~data$educ+data$IQ)

summary(lm3)
```
The $\tilde{\beta}_1$ and $\tilde{\beta}_2$ are equal to 0.03 and 0.005, respectively.

**(iv) Verify that $\tilde{\beta}_1=\hat{\beta}_1+\hat{\beta}_2\tilde{\delta}_1$.**

Given the estimated coefficientes, we have that

$$0.03+0.005(3.53)=0.05$$


Hence, the equality is satisfied.

