---
title: "Chapter 3 - Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "15/02/2022"
output: html_document
---

# Exercise 3.1

Upload package

```{r, warning=FALSE, message=FALSE}

library(lmreg)
library(wooldridge)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::bwght

```




**A problem of interest to health officials (and others) is to determine the effects of smoking during pregnancy on infant health**.
**One measure of infant health is birth weight; a birth weight that is too low can put an infant at risk for contracting various illnesses**.
**Since factors other than cigarette smoking that affect birth weight are likely to be correlated with smoking, we should take those **
**factors into account. For example, higher income generally results in access to better prenatal care, as well as better nutrition for**
**the mother. An equation that recognizes this is**

$$bwght=\beta_0+\beta_1cigs+\beta_2faminc+\varepsilon$$

**(i) What is the most likely sign for $\beta_2$?**

As family income increase, the birth weight of children is expected to increase as well, ceteris paribus. Hence, the expected sign of
$\beta_2$ is positive.

**(ii) Do you think cigs and faminc are likely to be correlated? Explain why the correlation**
**might be positive or negative.**

There's a variety of factors that influence a people to smoke. The correlation between quantity of cigarrestes smoked and family's income
might be positive or negative. Given that correlation does not imply causality, there's much more observable and unobservable factors that influence a people behavior in smoke or not smoke.

**(iii) Now, estimate the equation with and without faminc, using the data in BWGHT**
**.RAW. Report the results in equation form, including the sample size and**
**R-squared. Discuss your results, focusing on whether adding faminc substantially**
**changes the estimated effect of cigs on bwght.**

Regression with `faminc`

```{r}

est1<-lm(data$bwght~data$cigs+data$faminc, data)

summary(est1)


```
The estimated equation is given by $bwgth=116.97-0.46cigs+0.09faminc$.

The sample size and R-Squared are 1387 and 2.9\%, respectively.

The coefficients present the expected sign and are both statistically significant.

For each smoked cigar, the weight of children lowers 0.46 pounds, _ceteris paribus_.

For each $1 increase in family income, the weight increases 0.09 pounds, _ceteris paribus_.

Now, the estimate without `faminc`.

```{r}

est2<-lm(data$bwght~data$cigs)

summary(est2)

```

In this case, the coefficient associate to number of smoked cigs, is equal to -0.51. Impliyng in a little difference in relation to the first estimative.
