---
title: "Chapter 3 - Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "04/03/2022"
output: html_document
---

# Exercise 3.9

Upload packages

```{r, warning=FALSE, message=FALSE}
library(lmreg)
library(wooldridge)
```

Upload database

```{r}
data<-wooldridge::charity

```


**Use the data in CHARITY.RAW to answer the following questions**

**(i) Estimate the equation** 

$$gift=\beta_0+\beta_1mailsyear+\beta_2giftlast+\beta_3propresp+u$$


**by OLS and report the results in the usual way, including the sample size and**
**R-squared. How does the R-squared compare with that from the simple regression**
**that omits `giftlast` and `propresp`?**

```{r}
lm1<-lm(gift~mailsyear+giftlast+propresp, data)

summary(lm1)

lm2<-lm(gift~mailsyear, data)

summary(lm2)
```

The estimated equation is given by 
$$\widehat{gift}=-4.55+2.16mailsyear+0.005giftlast+15.35propresp$$

The variability in response variable `gift` is only 8.3% explained by the predictor variables.

In the simple regression estimation this value was 1.3%. Hence, the inclusion of predictor variables 
increases the predictability of the model.

**(ii) Interpret the coefficient on `mailsyear`. Is it bigger or smaller than the corresponding**
**simple regression coefficient?**

The coefficient of `mailsyear` gives the marginal increase in the variable `gifts` for each additional
mail sent. In the simple regression model this value is 2.64 against 2.14 in the multiple regression.

**(iii) Interpret the coefficient on `propresp`. Be careful to notice the units of measurement**
**of `propresp`.**

This coefficient measures, for a marginal increase in the `propresp`, the variation in mountant of `gifts`.

**(iv) Now add the variable `avggift` to the equation. What happens to the estimated effect**
**of `mailsyear`?**

```{r}
lm3<-lm(gift~mailsyear+giftlast+propresp+avggift,data)

summary(lm3)
```

In this case, the coefficient of `mailsyear` reduces from 2.16 to 1.20.

**(v) In the equation from part (iv), what has happened to the coefficient on giftlast?**
**What do you think is happening?**

The sign of coefficient of the variable `giflast` changes from positive to negative. Indicating a possible negative effect
of variable `giftlast` in a model with more exogenous variables.
