---
title: "Chapter 3 - Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "16/02/2022"
output: html_document
---

# Exercise 3.2

Upload packages

```{r, warning=FALSE, message= FALSE}

library(lmreg)
library(wooldridge)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::hprice1

attach(data)

```
**Use the data in HPRICE1.RAW to estimate the model**

$$price=\beta_0+\beta_1sqrft+\beta_2bedrms+\varepsilon$$
**where price is the house price measured in thousands of dollars.**

**(i) Write out the results in equation form.**

```{r}

lm1<-lm(price~sqrft+bdrms)

summary(lm1)

```

The estimated equation is given by $$price=-19.31+0.12sqrft+15.19bdrms$$

**(ii) What is the estimated increase in price for a house with one more bedroom, holding**
**square footage constant?**

For each additional bedroom, the price of the house increases \$15.2, _ceteris paribus_.

**(iii) What is the estimated increase in price for a house with an additional bedroom that**
**is 140 square feet in size? Compare this to your answer in part (ii).**

For a house with `sqrft=140` and an additional bedroom, the price is 

$$price=-19.31+0.12\times(140)+15.19 \times (1)=12.68$$
Hence, in this case, the estimated house price is $12,680.

**(iv) What percentage of the variation in price is explained by square footage and number**
**of bedrooms?**

This measure is given by R-Squared. Hence, is this case 63.1\% of variability in house price is explained by these variables.

**(v) The first house in the sample has sqrft = 2,438 and bdrms = 4. Find the predicted**
**selling price for this house from the OLS regression line.**

Substituing theses values in estimated equation, we obtain 

$$price=-19.31+0.12\times(2438)+15.2\times(4)=334.05$$

Hence, in this case, the estimated house price is $334,050.

**(vi) The actual selling price of the first house in the sample was $300,000 (so price 5**
**300). Find the residual for this house. Does it suggest that the buyer underpaid or**
**overpaid for the house?**

The residual is given by $\hat{\varepsilon}=price-\widehat{price}=300,00-334,05=-34,05$

It means that, buyer overpaid by the house.