---
title: "Chapter 3 - The Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "17/02/2022"
output: html_document
---

# Exercise 3.3

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::ceosal2

attach(data)

View(data)

```



**The file CEOSAL2.RAW contains data on 177 chief executive officers and can be used**
**to examine the effects of firm performance on CEO salary**

**(i) Estimate a model relating annual salary to firm sales and market value. Make the**
**model of the constant elasticity variety for both independent variables. Write the**
**results out in equation form.**

```{r}

lm1<-lm(log(salary)~log(sales)+log(mktval))

summary(lm1)

```
The estimated equation is given by $$\widehat{log(salary)}=4.62+0.16log(sales)+0.10log(mktval)$$

**(ii) Add profits to the model from part (i). Why can this variable not be included in**
**logarithmic form? Would you say that these firm performance variables explain**
**most of the variation in CEO salaries?**

```{r}

options(scipen=999) # To avoid scientific notation

lm2<-lm(log(salary)~log(sales)+log(mktval)+profits)

summary(lm2)

```

The variable `profits` cannot be added in log form, because there's negative values for this variable.

Based on R-Squared, these variables explained only 29.9\% of variability in CEO Salary.

**(iii) Add the variable ceoten to the model in part (ii). What is the estimated percentage**
**return for another year of CEO tenure, holding other factors fixed?**

```{r}

lm3<-lm(log(salary) ~ log(sales) + log(mktval)+ceoten+I(ceoten^2))

summary(lm3)

```


