---
title: "Chapter 3 - The Multiple Regression Analysis - Estimation"
author: "Thalles Quinaglia Liduares"
date: "21/02/2022"
output: html_document
---

# Exercise 3.4

Upload packages

```{r, warning=FALSE, message=FALSE}

library(wooldridge)
library(lmreg)
library(dplyr)

```

Upload database

```{r, warning=FALSE, message=FALSE}

data<-wooldridge::attend

attach(data)

```
**Use the data in ATTEND.RAW for this exercise.**
**(i) Obtain the minimum, maximum, and average values for the variables atndrte, priGPA, and ACT.**

The `min`, `max` and `mean` for the variable `atndrte` are given, respectively by

```{r}

atn_stat<-data %>%
          summarise(minimum = min(atndrte),
                    maximum = max(atndrte),
                    mean_value = round(mean(atndrte, na.rm=TRUE),2))
atn_stat

```
  
  
The `min`, `max` and `mean` for the variable `priGPA` are given, respectively by

```{r}

priGPA_stat<-data %>%
          summarise(minimum = min(priGPA),
                    maximum = max(priGPA),
                    mean_value = round(mean(priGPA, na.rm=TRUE),2))

priGPA_stat 

```

Finally, the `min`, `max` and `mean` for the variable `ACT` are given, respectively by

```{r}

ACT_stat<-data %>%
          summarise(minimum = min(ACT),
                    maximum = max(ACT),
                    mean_value = round(mean(ACT, na.rm=TRUE),2))

ACT_stat

```


**(ii) Estimate the model** 

$$atndrte=\beta_0+\beta_1 priGPA+ \beta_2 ACT + u$$

**and write the results in equation form. Interpret the intercept. Does it have a useful**
**meaning?**

```{r}

lm1<-lm(atndrte~priGPA+ACT)

summary(lm1)
```

The estimated equation is given by

$$\widehat{atndrte}=75.7+17.2 priGPA - 1.71 ACT$$

The intercept represents, the value of `atndrte` if `priGPA` and `ACT` are equal to zero, which not make pratical sense,
given that students spent at least some time in studies.

**Discuss the estimated slope coefficients. Are there any surprises?**

Given the estimated coefficients, for a marginal variation in `priGPA` the percentual increase in `atndrte` is 17.2%, which makes sense from the theoretical point of view, given that students who frequent more classes, tends to perform better in exams. Otherwise, the coefficient associated to ACT, is -1.71, which not presents the expected sign, given that students with higher `ACT` tends to frequent more classes.

**(iv) What is the predicted atndrte if priGPA = 3.65 and ACT = 20? What do you**
**make of this result? Are there any students in the sample with these values of the**
**explanatory variables?**

substituting theses values in estimated equation, we obtain 

$$\widehat{atndre}=75.7+17.2\times(3.65)-1.71 \times(20)=104.28$$
This value doesnt make sense, as `atndre` is the percentual value for attended classes by some student.

**(v) If Student A has priGPA = 3.1 and ACT = 21 and Student B has priGPA = 2.1**
**and ACT = 26, what is the predicted difference in their attendance rates?**

For student A: $\widehat{atndre}_{A}=75.7+17.2\times(3.1)-1.71 \times(21)=93.1$

For Student B: $\widehat{atndre}_{B}=75.7+17.2\times(2.1)-1.71 \times(26)=67.4$

Hence, the predicted difference is $\widehat{atndre}_{A}-\widehat{atndre}_{B}=93.1-67.4=25.7$
