---
title: "An introduction to econometrics - J.Wooldridge - Ch14 - Ex2"
author: "Thalles Quinaglia Liduares"
date: "03/04/2023"
output: html_document
---

Use CRIME4.RAW  for this exercise.

(i) Reestimate the unobserved effects model for crime in Example 13.9 but use fixed 
effects rather than differencing. Are there any notable sign or magnitude changes 
in the coefficients? What about statistical significance?

Upload package

```{r}
library(wooldridge)
library(plm)
```

Upload data

```{r}
data<-wooldridge::crime4
```
### Fixed effects regression
```{r}

crime_fe <- plm(crmrte ~ prbarr + prbconv + prbpris + avgsen + polpc, data = crime4, index = c("county","year"),
                model = "within")

```

### Results

```{r}
summary(crime_fe)
```


(ii) Add the logs of each wage variable in the data set and estimate the model by fixed 
effects. How does including these variables affect the coefficients on the criminal 
justice variables in part (i)?

### Add the logs of each wage variable

### Estimate the fixed effects model with logged wage variables

```{r}

crime_fe_logwage <- plm(crmrte ~ prbarr + prbconv + prbpris + avgsen + polpc  
                            +data$lwcon  
                            +data$lwfed
                            +data$lwfir
                            +data$lwloc
                            +data$lwmfg
                            +data$lwser
                            +data$lwsta
                            +data$lwtrd
                            +data$lwtuc, 
                            data = crime4, 
                            index = c("county", "year"),
                            model = "within")


```
### Results
```{r}
summary(crime_fe_logwage)
```


(iii) Do the wage variables in part (ii) all have the expected sign? Explain. Are they 
jointly significant?

### Test joint significance of wage variables

```{r}

library(car)
linearHypothesis(crime_fe_logwage, c("data$lwcon=0"  
                            ,"data$lwfed=0"
                            ,"data$lwfir=0"
                            ,"data$lwloc=0"
                            ,"data$lwmfg=0"
                            ,"data$lwser=0"
                            ,"data$lwsta=0"
                            ,"data$lwtrd=0"
                            ,"data$lwtuc=0"), vcov = vcovHC(crime_fe_logwage, type = "HC1"))
```


The test statistic indicates that we can reject the null hypothesis and conclude that the wage variables are jointly significant at conventional levels.